### 2023-10-27 README.qmd
Add README.qmd, render in _targets, and tar_make()

---
format: gfm
---

# ManyEcoEvo <img src="man/figures/ManyEcoEvoHex.jpg" align="right" alt="" width="120" />

The `ManyEcoEvo` package provides a suite of functions for:

- Summarising, analysing and visualising the ManyEcoEvo dataset from 
*Gould et al.*[^1]
- Tidying and cleaning many-analyst style data for further analysis
- Reproducing the analysis in *Gould et al.* using your own many-analyst style data

> Note that the manuscript source-code for *Gould et al.* is located in a separate repository at [https://github.com/egouldo/ManyAnalysts](https://github.com/egouldo/ManyAnalysts), which can be viewed at [https://egouldo.github.io/ManyAnalysts/](https://egouldo.github.io/ManyAnalysts/).

## Installation

`ManyEcoEvo::` can be installed using [`devtools::`](https://devtools.r-lib.org) from GitHub with:

```{r eval=FALSE}
devtools::install_github("egouldo/ManyEcoEvo")
```

# Regenerating the ManyEcoEvo dataset

The data processing and analysis can be freely reproduced with the help of the [`targets::`](https://github.com/ropensci/targets) package. Please see the documentation at [https://docs.ropensci.org/targets/](https://docs.ropensci.org/targets/) for further detail.

Should you wish to completely reproduce the dataset generation and analysis in *Gould et al.*, complete the following steps:

1. Clone or download  [https://github.com/egouldo/this repository](https://github.com/egouldo/ManyEcoEvo)
2. Run `renv::restore()` to load the packages used in the analysis pipeline locally on your machine
3. Run `tar_destroy()` to remove any record and caches of existing targets
3. Run `targets::tar_make()` in your console, depending on the power of your machine, the analysis pipeline will take between 2 and 7 minutes to execute (plus or minus some!)
4. You can view a table of all targets in the pipeline by running `targets::tar_meta()`
5. To interact with objects or 'targets' within the analysis pipeline, call `targest::tar_load()` or `targets::tar_read()`:

```{r echo=FALSE}
suppressPackageStartupMessages(library(targets))
```

```{r}
targets::tar_read("ManyEcoEvo")
```

## License

This software is licensed with the GNU GPL 3 license [![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)

## Contributing

This package is released with a [Contributor Code of Conduct](https://github.com/egouldo/ManyEcoEvo/blob/aa2b9dcb6462f35ce873418e0b9c9697cf0b2f24/CODE_OF_CONDUCT.md) [![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](code_of_conduct.md)

## Citation

[^1]: Gould, E., Fraser, H., Parker, T. *et al.* (2023). Same data, different analysts: Variation in effect sizes due to analytical decisions in ecology and evolutionary biology [Preprint]. Ecology and Evolutionary Biology. https://doi.org/10.32942/X2GG62

### 2023-10-27 _targets.R

@@ -231,6 +231,8 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                            meta_analyse_datasets() #TODO requires col exclusion_set from generate_exclusino_subsets() but don't need that fun in this pipeline anymore
      ),
      targets::tar_target( name = ManyEcoEvo_yi_viz,
-                          command = make_viz(ManyEcoEvo_yi_results))
+                          command = make_viz(ManyEcoEvo_yi_results)),
+     tarchetypes::tar_quarto(name = README,
+                             path = "README.qmd")
      # tarchetypes::tar_quarto(full_analysis, "analysis/analysis_revised_data.qmd")
 )

### 2023-10-27 README.qmd
Add package citation info in README and render with tar_make()

@@
 
-# ManyEcoEvo <img src="man/figures/ManyEcoEvoHex.jpg" align="right" alt="" width="120" />
+# ManyEcoEvo <img src="man/figures/ManyEcoEvoHex.jpg" align="right" width="120"/>
 
@@
 
-- Summarising, analysing and visualising the ManyEcoEvo dataset from 
-*Gould et al.*[^1]
+-   Summarising, analysing and visualising the ManyEcoEvo dataset from *Gould et al.*[^1]
 -   Tidying and cleaning many-analyst style data for further analysis
@@
 
-> Note that the manuscript source-code for *Gould et al.* is located in a separate repository at [https://github.com/egouldo/ManyAnalysts](https://github.com/egouldo/ManyAnalysts), which can be viewed at [https://egouldo.github.io/ManyAnalysts/](https://egouldo.github.io/ManyAnalysts/).
+> Note that the manuscript source-code for *Gould et al.* is located in a separate repository at <https://github.com/egouldo/ManyAnalysts>, which can be viewed at <https://egouldo.github.io/ManyAnalysts/>.
 
@@
 The data processing and analysis can be freely reproduced with the help of the [`targets::`](https://github.com/ropensci/targets) package.
-Please see the documentation at [https://docs.ropensci.org/targets/](https://docs.ropensci.org/targets/) for further detail.
+Please see the documentation at <https://docs.ropensci.org/targets/> for further detail.
 
@@
 3.  Run `tar_destroy()` to remove any record and caches of existing targets
-3. Run `targets::tar_make()` in your console, depending on the power of your machine, the analysis pipeline will take between 2 and 7 minutes to execute (plus or minus some!)
-4. You can view a table of all targets in the pipeline by running `targets::tar_meta()`
-5. To interact with objects or 'targets' within the analysis pipeline, call `targest::tar_load()` or `targets::tar_read()`:
+4.  Run `targets::tar_make()` in your console, depending on the power of your machine, the analysis pipeline will take between 2 and 7 minutes to execute (plus or minus some!)
+5.  You can view a table of all targets in the pipeline by running `targets::tar_meta()`
+6.  To interact with objects or 'targets' within the analysis pipeline, call `targest::tar_load()` or `targets::tar_read()`:
 
@@
 
+```         
+To cite package ‘ManyEcoEvo’ in publications use:
+
+  Gould E, Fraser H, Nakagawa S, Parker T (2023). _ManyEcoEvo: Meta-analyse
+  data from 'Many-Analysts' style studies_. R package version 1.0.0,
+  <https://github.com/egouldo/ManyEcoEvo>.
+
+A BibTeX entry for LaTeX users is
+
+  @Manual{,
+    title = {ManyEcoEvo: Meta-analyse data from 'Many-Analysts' style studies},
+    author = {Elliot Gould and Hannah S. Fraser and Shinichi Nakagawa and Timothy H. Parker},
+    year = {2023},
+    note = {R package version 1.0.0},
+    url = {https://github.com/egouldo/ManyEcoEvo},
+  }
+```
+
 [^1]: Gould, E., Fraser, H., Parker, T.
     *et al.* (2023).
-Same data, different analysts: Variation in effect sizes due to analytical decisions in ecology and evolutionary biology [Preprint].
+    Same data, different analysts: Variation in effect sizes due to analytical decisions in ecology and evolutionary biology \[Preprint\].
     Ecology and Evolutionary Biology.

### 2023-10-27 README.qmd
Add link to renv:: and rebuild README
Move badge positions to top, add Zenodo badge and rerender

@@
 ---
+
+[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.10046153.svg)](https://doi.org/10.5281/zenodo.10046153) [![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0) [![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](code_of_conduct.md)
 
@@
 1.  Clone or download [https://github.com/egouldo/this repository](https://github.com/egouldo/ManyEcoEvo)
-2.  Run `renv::restore()` to load the packages used in the analysis pipeline locally on your machine
+2.  Run `renv::restore()` to load the packages used in the analysis pipeline locally on your machine (see [`renv::`]https://rstudio.github.io/renv/index.html) for details)
 3.  Run `tar_destroy()` to remove any record and caches of existing targets
@@
 
-This software is licensed with the GNU GPL 3 license [![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
+This software is licensed with the GNU GPL 3 license.
 
@@
 
-This package is released with a [Contributor Code of Conduct](https://github.com/egouldo/ManyEcoEvo/blob/aa2b9dcb6462f35ce873418e0b9c9697cf0b2f24/CODE_OF_CONDUCT.md) [![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](code_of_conduct.md)
+This package is released with a [Contributor Code of Conduct](https://github.com/egouldo/ManyEcoEvo/blob/aa2b9dcb6462f35ce873418e0b9c9697cf0b2f24/CODE_OF_CONDUCT.md).
 

### 2023-11-09 manuscript/manuscript/manuscript.Rmd
Set up draft manuscript skeleton and metadata, and package vignettes.

---
# Example from https://joss.readthedocs.io/en/latest/submitting.html
title: 'ManyEcoEvo: an R package for working with the "Same Data, Different Analysts" Project in Ecology and Evolutionary Biology, and other many-analyst style data'
tags:
  - R
  - meta-analysis
  - metaresearch
  - ecology
  - evolutionary biology
  - many-analysts
authors:
  - name: Elliot Gould
    orcid: 0000-0003-0872-7098
    affiliation: "1" 
  - name: Hannah S. Fraser
    orcid: 0000-0000-0000-0000
    affiliation: "1"
  - name: Shinichi Nakagawa
    orcid: 0000-0000-0000-0000
    affiliation: "2"
  - name: Timothy H. Parker
    orcid: 0000-0000-0000-0000
    affiliation: "3"
affiliations:
 - name: The University of Melbourne
   index: 1
 - name: The University of New South Wales
   index: 2
 - name: Whitman College
   index: 3
citation_author: Gould and Fraser et al. 
date: "`r Sys.Date()`"
year: 2023
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---

# Summary

# Statement of Need

# Same Data, Different Analysts: variation in effect sizes due to analytical decisions in ecology and evolutionary biology.

# Acknowledgements

We acknowledge the contributions of all 246 analysts and co-authors of Gould et al. (2023). EG is supported by an Australian Government Research Training Program Scholarship.

- [ ] HF?
- [ ] SN?
- [ ] TP?

# References

### 2023-11-10 manuscript/manuscript/manuscript.Rmd
Add text to summary section and statement of need section

@@
 
+Typical scientific approaches proceed with a single team, and one analytic specification, or at most several specifications implemented.
+Thus the effect of alternative defensible analytic choices that could have been implemented is never known, either because alternative specifications aren't explored, or worse, because analysts / authors implement them but do not publish alternative analysis specifications.
+However, we know from simulations and case studies that researcher degrees of freedom can result in spurious findings [@simmons2011], and these researcher degrees of freedom are susceptible to publication bias, p-hacking and other questionable research practice.
+Similarly, specification curve analysis of published findings have demonstrated that the published conclusion had empirical support from only a small sample of the overall plausible specifications (evidence of spurious findings, and possibly publication bias and p-hacking) [@Simonsohn2019].
+
+Many-analyst studies are a format of crowd-sourced scientific analysis [@schweinsberg2021], where analysts simultaneously, but independently, research the same research question, using the same dataset [@Voracek2019; @silberzahn2018].
+Many-analyst studies demonstrate how subjective, often arbitrary and usually defensible analysis decisions may influence research results [@silberzahn2018] due to either disagreement among researchers or due to analytic uncertainty about choices such as which observations to include and what data-analysis strategy is most appropriate [@Voracek2019].
+
+The *ManyEcoEvo* project is a many-analyst study that aimed to empirically explore the variation in effect sizes and model predictions generated by analytical decisions of different researchers within ecology and evolutionary biology [@gould2023].
+174 analyst teams, comprising 246 analysts, independently investigated the answers to two pre-specified research questions using two previously unpublished datasets, one from conservation ecology, and one from evolutionary biology.
+Analysts investigating the evolutionary biology dataset examined the effect of sibling number and nestling growth of blue tits (*Cyanistes caeruleus*), while analysts investigating the conservation ecology dataset examined the relationship between grass cover and *Eucalyptus* tree seedling recruitment.
+The ManyEcoEvo project quantified the variation in results among analyses using meta-analysis and additionally sought to understand how features of studies such as, variable selection, random effects structures, qualitative and numeric ratings of the methods by peer-reviewers, influenced deviation from the meta-analytic mean.
+
+*ManyEcoEvo* is an R package[@RCoreTeam2022] designed to *facilitate the analysis of* a many-analyst study in ecology and evolutionary biology, the *ManyEcoEvo Project* [@gould2023].
+The purpose of *ManyEcoEvo* is to reproducibly implement the analysis and presentation of results for Gould *et al.* [-@gould2023] such that the 246 analysts as well as other interested researchers may independently reproduce the study's findings.
+The package also aims to facilitate re-analyses and replications of Gould *et al.* [-@gould2023], as well as facilitating the analysis of similar many-analyst style datasets.
+
+All raw data sets provided to independent teams for analysis, as well data collected on the analyses themselves are archived at **OSF Link1, OSF Link2,** respectively, and are provided in the GitHub repository for the package **(INSERT LINK)**, archived on Zenodo **(INSERT CITATION).** The ManyEcoEvo project contains tools for data-cleaning and processing tasks encountered when working with with many-analyst style data, functions for implementing and reproducing the analysis described inGould *et al.* [-@gould2023], establishes a structured workflow that facilitates re-analyses and replications of Gould *et al.* [-@gould2023] as well as implementation for new many-analyst studies, including a planned extension of the ManyEcoEvo project.
+
 # Statement of Need
+
+The *ManyEcoEvo* package was created to implement the analysis for the 'Same Data, Many Analysts in Ecology and Evolutionary Biology' project [@gould2023] and to allow the 246 co-authors and other interested researchers to computationally reproduce our analysis.
+Following [@Marwick2018], [@Vuorre2021] and [@Filazzola2022], we opted to develop this research compendium as an R package as we find it best encapsulates the principles of 'clean code' for effective communication of the science, and therefore facilitates future reproduction, replication and potential synthesis [R packages as research compendia].
+The results of some many-analyst studies have been controversial, yielding re-analyses criticising the original implementation of some many-analyst studies.
+For example, [@Auspurg2021] re-analysed part of the seminal 'Red-Card' many-analyst study examining the influence of whether referees were more likely to give red cards to soccer players with dark skin tone than those with light skin tone [@silberzahn2018].
+By providing the code and data for Gould *et al.* [-@gould2023] the *ManyEcoEvo* package, we aim to facilitate computational reproductions by others in order to verify our results.
+We also aim to facilitate analytic reproductions of this study, wherein *ManyEcoEvo* can be used to re-run the analysis in Gould *et al.* [-@gould2023] with slightly different methods, or subsets of data in order to verify and examine the robustness of our findings.
 
@@
 
-We acknowledge the contributions of all 246 analysts and co-authors of Gould et al. (2023). EG is supported by an Australian Government Research Training Program Scholarship.
+We acknowledge the contributions of all 246 analysts and co-authors of Gould et al. (2023).
+EG is supported by an Australian Government Research Training Program Scholarship.
 

### 2023-11-10 manuscript/manuscript/manuscript.Rmd
Complete statement of need section

@@
 
+The last ten years has seen the growing emergence of many-analyst projects, [e.g.
+@silberzahn2018; @botvinik-nezer2020; @huntington-klein2021; @schweinsberg2021; @breznau2022; @hoogeveen2022many; @coretta2023], predominantly in the disciplines of psychology and social and behavioural sciences, however we expect more of these types of studies to be published into the near future across other disciplines.
+Moreover, collaborative and distributed big team open science projects are becoming increasingly common in ecology and evolutionary biology (e.g.
+NutNet <https://nutnet.org/index.php/>, DragNet, ManyBirds <http://themanybirds.com>) as well as other disciplines (ManyBabies **CITE**, ManyPrimates **CITE**) which pose computationally analogous data-manipulation and analysis problems to the many-analyst workflow addressed by the *ManyEcoEvo* approach.
+While *ManyEcoEvo* was designed for the ManyEcoEvo project, the structured approach it employs establishes a workflow that can be generalised and applied to new many-analyst style data, facilitating replication of Gould *et al.* [-@gould2023], in addition to computational reproduction [@Stoudt2021], as well as new analyses of many-analyst type studies.
+
+We are not aware of any R packages or software in other languages exclusively focussed on facilitating many-analyst style studies.
+Existing many-analyst code if shared, is written as R scripts particular to that study's analysis (e.g.
+<https://github.com/manybabies/mb1-analysis-public>, <https://github.com/many-speech-analyses/many_analyses>).
+However, there are a range of existing packages with select functionality that addresses various components of many-analyst style analyses, namely meta-analysis, its associated preparation and visualisation, as well as the visualisation component of [specification curve analysis] / [multiverse analysis] ([@Simonsohn2020], [@Steegen2016]).
+Following the collection of results from teams conducting independent analyses, the data must be 1.
+cleaned and prepared for 2.
+meta-analysis and other model analysis, which is then 3.
+subjected to model checking, statistic extraction and visualisation [@aczel2021].
+
+We provide a suite of miscellaneous functions for data cleaning and processing tasks that we expect to be common to the sorts of data collected by many-analyst style studies.
+This was the most time and effort-intensive aspect of the analysis in Gould *et al.* [-@gould2023], and we hope these functions will ease the burden on future researchers conducting many-analyst studies.
+
+*ManyEcoEvo* provides custom functions to calculate standardize effect sizes in the form of Fishers' Z correlation scores in preparation for meta-analysis.
+While some existing functions exist within other packages (e.g.
+`DescTools::FishersZ()`, `DiagTest3Grp::FisherZ.var()`), the method for calculating variance of the standardized effect size in Gould *et al.* [-@gould2023] differed slightly see `INSERT FUNCTION NAME`, and we wished to avoid reliance on too many external packages (Wickham & Bryan, 2023: **Chapter 10.1**).
+Should *ManyEcoEvo* users wish to deviate from the effect-size standardisation method used in Gould *et al.* [-@gould2023], they are free to use their own functions provided by other software or custom functions (See **Harrer et al.
+2022** chapter 3 for a range of R snippets that calculate various effect sizes).
+
+`meta` (**CITE**) and `metafor` (**cite**) R packages are the two most commonly used softwares for undertaking meta-analysis in R [@lortie2020].
+We provide functions for fitting the exact meta-analysis models used in Gould *et al.* [-@gould2023], which were implemented with the *metafor* package, however *ManyEcoEvo* users are free to supply alternative model-fitting functions should they wish to deviate from these specified models.
+After model-fitting and analysis, model checking and extraction of model fit and heterogeneity statistics is implemented using a range of existing packages, including: `performance::`, `broom.mixed::`, `metafor::`.
+*ManyEcoEvo* also draws on existing visualisation packages to implement forest plots (`ggforest::)`, funnel plots (`metafor::`), and s [specification curve analysis] plots to examine the influence of analysis specifications on variation in analysis outcomes (`specr::`).
+Select functions from the above packages have been thoughtfully abstracted and coded into wrapper functions according to a principled and structured workflow (described below) for ease of application and generalisation to alternative datasets.
+
 # Same Data, Different Analysts: variation in effect sizes due to analytical decisions in ecology and evolutionary biology.
@@
 
-We acknowledge the contributions of all 246 analysts and co-authors of Gould et al. (2023).
+We acknowledge the contributions of all 246 analysts and co-authors of Gould *et al. [-@gould2023]* please see the original manuscript for a full list of contributors to the ManyEcoEvo project.
+
 EG is supported by an Australian Government Research Training Program Scholarship.

### 2023-11-10 manuscript/manuscript/manuscript.Rmd
Complete first draft of manuscript introduction

@@
 bibliography: paper.bib
-output: rticles::joss_article
+output: 
+  # word_document: default
+  rticles::joss_article:
+    journal: JOSS
 csl: apa.csl
-journal: JOSS
 ---
@@
 
-*ManyEcoEvo* is an R package[@RCoreTeam2022] designed to *facilitate the analysis of* a many-analyst study in ecology and evolutionary biology, the *ManyEcoEvo Project* [@gould2023].
+*ManyEcoEvo* is an R package [@RCoreTeam2022] designed to *facilitate the analysis of* a many-analyst study in ecology and evolutionary biology, the *ManyEcoEvo Project* [@gould2023].
 The purpose of *ManyEcoEvo* is to reproducibly implement the analysis and presentation of results for Gould *et al.* [-@gould2023] such that the 246 analysts as well as other interested researchers may independently reproduce the study's findings.
@@
 
-All raw data sets provided to independent teams for analysis, as well data collected on the analyses themselves are archived at **OSF Link1, OSF Link2,** respectively, and are provided in the GitHub repository for the package **(INSERT LINK)**, archived on Zenodo **(INSERT CITATION).** The ManyEcoEvo project contains tools for data-cleaning and processing tasks encountered when working with with many-analyst style data, functions for implementing and reproducing the analysis described inGould *et al.* [-@gould2023], establishes a structured workflow that facilitates re-analyses and replications of Gould *et al.* [-@gould2023] as well as implementation for new many-analyst studies, including a planned extension of the ManyEcoEvo project.
+All raw data sets and metadata provided to independent teams for analysiss are publicly archived at <https://osf.io/qjzby> and <https://osf.io/hdv8m>, respectively.
+Analyst survey responses and results are provided in the package GitHub repository (<https://github.com/egouldo/ManyEcoEvo/>), which is also archived on Zenodo (<https://doi.org/10.5281/zenodo.10046153>).
+*ManyEcoEvo* contains tools for data-cleaning and processing tasks encountered when working with with many-analyst style data, functions for implementing and reproducing the analysis described inGould *et al.* [-@gould2023], establishes a structured workflow that facilitates re-analyses and replications of Gould *et al.* [-@gould2023] as well as implementation for new many-analyst studies, including a planned extension of the ManyEcoEvo project.
 
@@
 Moreover, collaborative and distributed big team open science projects are becoming increasingly common in ecology and evolutionary biology (e.g.
-NutNet <https://nutnet.org/index.php/>, DragNet, ManyBirds <http://themanybirds.com>) as well as other disciplines (ManyBabies **CITE**, ManyPrimates **CITE**) which pose computationally analogous data-manipulation and analysis problems to the many-analyst workflow addressed by the *ManyEcoEvo* approach.
+NutNet/DragNet <https://nutnet.org/index.php/>, ManyBirds <http://themanybirds.com>) as well as other disciplines [ManyBabies @ManyBabies , ManyPrimates @ManyPrimates] which pose computationally analogous data-manipulation and analysis problems to the many-analyst workflow addressed by the *ManyEcoEvo* approach.
 While *ManyEcoEvo* was designed for the ManyEcoEvo project, the structured approach it employs establishes a workflow that can be generalised and applied to new many-analyst style data, facilitating replication of Gould *et al.* [-@gould2023], in addition to computational reproduction [@Stoudt2021], as well as new analyses of many-analyst type studies.
@@
 <https://github.com/manybabies/mb1-analysis-public>, <https://github.com/many-speech-analyses/many_analyses>).
-However, there are a range of existing packages with select functionality that addresses various components of many-analyst style analyses, namely meta-analysis, its associated preparation and visualisation, as well as the visualisation component of [specification curve analysis] / [multiverse analysis] ([@Simonsohn2020], [@Steegen2016]).
+However, there are a range of existing packages with select functionality that addresses various components of many-analyst style analyses, namely meta-analysis, its associated preparation and visualisation, as well as the visualisation component of specification curve analysis / multiverse analysis [@Simonsohn2020; @Steegen2016].
 Following the collection of results from teams conducting independent analyses, the data must be 1.
@@
 *ManyEcoEvo* provides custom functions to calculate standardize effect sizes in the form of Fishers' Z correlation scores in preparation for meta-analysis.
-While some existing functions exist within other packages (e.g.
-`DescTools::FishersZ()`, `DiagTest3Grp::FisherZ.var()`), the method for calculating variance of the standardized effect size in Gould *et al.* [-@gould2023] differed slightly see `INSERT FUNCTION NAME`, and we wished to avoid reliance on too many external packages (Wickham & Bryan, 2023: **Chapter 10.1**).
-Should *ManyEcoEvo* users wish to deviate from the effect-size standardisation method used in Gould *et al.* [-@gould2023], they are free to use their own functions provided by other software or custom functions (See **Harrer et al.
-2022** chapter 3 for a range of R snippets that calculate various effect sizes).
+While some existing functions exist within other packages [e.g.
+`DescTools::FishersZ()` @DescTools, `DiagTest3Grp::FisherZ.var()` @luo2012diagtest3grp], the method for calculating variance of the standardized effect size in Gould *et al.* [-@gould2023] differed slightly, and we wished to avoid reliance on too many external packages [@wickham2023r, Chapter 10.1].
+Should *ManyEcoEvo* users wish to deviate from the effect-size standardisation method used in Gould *et al.* [-@gould2023], they are free to use their own functions provided by other software or custom functions [@harrer2021, see chapter 3 for a range of R code to calculate various effect sizes].
 
-`meta` (**CITE**) and `metafor` (**cite**) R packages are the two most commonly used softwares for undertaking meta-analysis in R [@lortie2020].
-We provide functions for fitting the exact meta-analysis models used in Gould *et al.* [-@gould2023], which were implemented with the *metafor* package, however *ManyEcoEvo* users are free to supply alternative model-fitting functions should they wish to deviate from these specified models.
-After model-fitting and analysis, model checking and extraction of model fit and heterogeneity statistics is implemented using a range of existing packages, including: `performance::`, `broom.mixed::`, `metafor::`.
-*ManyEcoEvo* also draws on existing visualisation packages to implement forest plots (`ggforest::)`, funnel plots (`metafor::`), and s [specification curve analysis] plots to examine the influence of analysis specifications on variation in analysis outcomes (`specr::`).
+`metafor` [@Viechtbauer:2010ks; @Viechtbauer2017] and `meta` [@Balduzzi2019] R packages are the two most commonly used softwares for undertaking meta-analysis in R [@lortie2020].
+We provide functions for fitting the exact meta-analysis models used in Gould *et al.* [-@gould2023], which were implemented with the *metafor* package [@Viechtbauer2017], however *ManyEcoEvo* users are free to supply alternative model-fitting functions should they wish to deviate from these specified models.
+After model-fitting and analysis, model checking and extraction of model fit and heterogeneity statistics is implemented using a range of existing packages, including: `performance::` [@ludecke2021], `broom.mixed::` [@Bolker2022], `metafor::` [@Viechtbauer2017].
+*ManyEcoEvo* also draws on existing visualisation packages to implement forest plots [`ggforestplot::`, @ggforestplot; @orchaRd], funnel plots [`metafor::` @Viechtbauer2017], and specification curve analysis plots [`specr::` @Masur2020 ] to examine the influence of analysis specifications on variation in analysis outcomes.
 Select functions from the above packages have been thoughtfully abstracted and coded into wrapper functions according to a principled and structured workflow (described below) for ease of application and generalisation to alternative datasets.
 
-# Same Data, Different Analysts: variation in effect sizes due to analytical decisions in ecology and evolutionary biology.
+# Same Data, Different Analysts: variation in effect sizes due to analytical decisions in ecology and evolutionary biology
+
+This is the body of the manuscript that will provide a short example of the claims about functionality I've made in the previous sections using the ManyEcoEvo analysis pipeline for correlation coefficients.
 

### 2023-11-15 R/summarise_review_data.R
#24 add new functions to summarise review data

@@ -1,0 +1,153 @@
+#' Title
+#'
+#' @param ManyEcoEvo 
+#' @param ManyEcoEvo_results 
+#' @param ManyEcoEvo_yi_results 
+#'
+#' @return
+#' @export
+#' @importFrom dplyr filter
+#' @importFrom dplyr select
+#' @importFrom tidyr unnest
+#' @importFrom dplyr mutate
+#' @importFrom dplyr rename
+#' @importFrom dplyr group_by
+#' @importFrom dplyr distinct
+#' @importFrom magrittr "%>%"
+#' @importFrom dplyr right_join
+#' @importFrom purrr map_dfr
+#' @importFrom purrr set_names
+#' @importFrom dplyr ends_with
+#' @importFrom broom tidy
+#' @import metafor
+#'
+#' @examples
+#' summarise_reviews(ManyEcoEvo, ManyEcoEvo_results,ManyEcoEvo_yi_results)
+summarise_reviews <- function(ManyEcoEvo, ManyEcoEvo_results, ManyEcoEvo_yi_results) {
+  review_data <- 
+    ManyEcoEvo %>% #TODO check that OK across all summarise code... was added after HF created original code
+    ungroup %>% 
+    select(data, -dataset) %>% 
+    unnest(data) %>% 
+    select(ends_with("_id"), id_col, dataset, review_data) %>% 
+    unnest(review_data)
+  
+  effect_ids <- ManyEcoEvo_results %>% 
+    filter(exclusion_set == "complete", 
+           publishable_subset == "All") %>% 
+    select(MA_mod, effects_analysis) %>% 
+    group_by(estimate_type, dataset) %>% 
+    mutate(tidy_mod = map(MA_mod, 
+                          ~ broom::tidy(.x, 
+                                        conf.int = TRUE, 
+                                        include_studies = TRUE) %>% 
+                            rename(study_id = term)), .keep = "none") %>% 
+    unnest(tidy_mod) %>% 
+    filter(type == "study") %>% 
+    ungroup %>% 
+    select(study_id) %>% 
+    rename(id_col = study_id) %>% #TODO duplicates for "Bell-2-2-1" and "Bonalbo-1-1-1 WHY?
+    distinct()
+  
+  prediction_ids <- ManyEcoEvo_yi_results %>% #TODO Euc mod_data_logged not here!
+    filter(exclusion_set == "complete", 
+           # dataset == "blue tit"
[…]

### 2023-11-15 R/summarise_variable_counts.R
#24 add missing importFrom roxygen tags

@@ -25,6 +25,8 @@
 #' @importFrom tidyr pivot_longer
 #' @importFrom purrr map_dfr
 #' @importFrom purrr set_names
+#' @importFrom dplyr ends_with
+#' @importFrom broom tidy
 #' @author Hannah S. Fraser
 #' @author Elliot Gould
 #' @family Multi-dataset Wrapper Functions
@@ -48,9 +50,10 @@ summarise_variable_counts <- function(ManyEcoEvo, ManyEcoEvo_results, ManyEcoEvo
                           ~ broom::tidy(.x, 
                                         conf.int = TRUE, 
                                         include_studies = TRUE) %>% 
-                            rename(study_id = term)), .keep = "none") %>% 
+                            rename(study_id = term)), 
+           .keep = "none") %>% 
     unnest(tidy_mod) %>% 
-    filter(type =="study") %>% 
+    filter(type == "study") %>% 
     ungroup %>% 
     select(study_id) %>% 
     rename(id_col = study_id) %>% #TODO duplicates for "Bell-2-2-1" and "Bonalbo-1-1-1 WHY?
@@ -65,7 +68,8 @@ summarise_variable_counts <- function(ManyEcoEvo, ManyEcoEvo_results, ManyEcoEvo
     mutate(tidy_mod = map(MA_mod, 
                           ~ broom::tidy(.x, conf.int = TRUE, include_studies = TRUE) %>% 
                             rename(study_id = term)), .keep = "none") %>% 
-    unnest(tidy_mod) %>% filter(type == "study") %>% 
+    unnest(tidy_mod) %>% 
+    filter(type == "study") %>% 
     ungroup %>% 
     select(study_id) %>% 
     rename(id_col = study_id) %>% 

### 2023-11-15 R/summarise_review_data.R
#24 forgot to calc sd for summarise_analyses_by_reviewer, complete @param and @return doc for summarise_reviews()

@@ -1,10 +1,12 @@
-#' Title
+#' Summarise Peer-Reviews
+#' 
+#' Calculates summary statistics (`mean`, `sd`, `min`, `max`) of both the number of analyses peer-reviewed by each reviewer, and the number of reviews received by each analysis.
 #'
-#' @param ManyEcoEvo 
-#' @param ManyEcoEvo_results 
-#' @param ManyEcoEvo_yi_results 
+#' @param ManyEcoEvo A tibble of `ManyEcoEvo`
+#' @param ManyEcoEvo_results A tibble of `ManyEcoEvo_results`
+#' @param ManyEcoEvo_yi_results A tibble of `ManyEcoEvo_yi_results`
 #'
-#' @return
+#' @return A named list of length two of `summarised_data_analyses` containing a tibble of summary statistics for each outcome `subset` (`effects` or `predictions`) generated by [summarise_analyses_by_reviewer()], and `summarised_data_reviews` containing a tibble of sumary statistics for each outcome `subset`, for each `dataset` generated by [summarise_reviews_per_analysis()].
 #' @export
 #' @importFrom dplyr filter
 #' @importFrom dplyr select
@@ -117,6 +119,7 @@ summarise_analyses_by_reviewer <- function(review_data) {
     group_by(ReviewerId) %>% 
     summarise(analyses = n_distinct(response_id)) %>% 
     summarise(mean = mean(analyses),
+              sd = sd(analyses),
               min = min(analyses),
               max = max(analyses)) 
 }

### 2023-11-15 R/summarise_review_data.R
#24 add author info and @family tag for summarise_reviews()

@@ -22,6 +22,9 @@
 #' @importFrom dplyr ends_with
 #' @importFrom broom tidy
 #' @import metafor
+#' @author Hannah S. Fraser
+#' @author Elliot Gould
+#' @family Multi-dataset Wrapper Functions
 #'
 #' @examples
 #' summarise_reviews(ManyEcoEvo, ManyEcoEvo_results,ManyEcoEvo_yi_results)

### 2023-11-15 R/summarise_review_data.R
#24 use roxygen comment for example

@@ -139,13 +139,13 @@ summarise_analyses_by_reviewer <- function(review_data) {
 #' @importFrom magrittr "%>%"
 #'
 #' @examples
-# ManyEcoEvo %>%
-# ungroup %>%
-# select(data, -dataset) %>%
-# unnest(data) %>%
-# select(ends_with("_id"), id_col, dataset, review_data) %>%
-# unnest(review_data) %>%
-# summarise_reviews_per_analysis()
+#' ManyEcoEvo %>%
+#' ungroup %>%
+#' select(data, -dataset) %>%
+#' unnest(data) %>%
+#' select(ends_with("_id"), id_col, dataset, review_data) %>%
+#' unnest(review_data) %>%
+#' summarise_reviews_per_analysis()
 summarise_reviews_per_analysis <- function(review_data) {
   # number of times analyses reviewed across all datasets
   review_data %>% 

### 2023-11-15 R/summarise_analysis_types.R
#24 complete adding data summary table functions

@@ -1,6 +1,10 @@
 #' Summarise Analysis Types
 #' @description
-#' Generates a summary of the number of analysis teams, total analyses, models with normal error distributions, mixed effects modls, and models developed using Bayesian statistical methods for a given analysis type.
+#' Generates a summary of the number of analysis teams, total analyses, models with normal error distributions, mixed effects models, and models developed using Bayesian statistical methods for a given analysis type.
+#' 
+#' @details
+#' Applies both [count_binary_coded_features()] and [count_teams_analyses()] to generate data summaries.
+#' 
 #' 
 #' @param ManyEcoEvo_results A tibble of `ManyEcoEvo_results`
 #' @param ManyEcoEvo_yi_results A tibble of `ManyEcoEvo_yi_results`

### 2023-11-15 R/summarise_conclusions.R

@@ -1,5 +1,8 @@
 #' Summarise counts of qualitative conclusions across all datasets
-#'
+#' 
+#' @details
+#' Data summary is generated with [summarise_conclusions_data()].
+#' 
 #' @param ManyEcoEvo_results A tibble of `ManyEcoEvo_results`
 #' @param ManyEcoEvo_yi_results A tibble of `ManyEcoEvo_yi_results`
 #' @param ManyEcoEvo A tibble of `ManyEcoEvo`

### 2023-11-15 R/summarise_model_composition.R

@@ -2,6 +2,10 @@
 #' @description
 #' Calculate descriptive statistics (mean, sd, min, max) for number of fixed effects, number of random effects, number of interactions and sample size of models for each dataset across both out of sample predictions and standardized corelation coefficients.
 #' 
+#' @details
+#' Generates summary data with [summarise_model_composition_data()].
+#' 
+#' 
 #' @param ManyEcoEvo_results A tibble of `ManyEcoEvo_results`
 #' @param ManyEcoEvo_yi_results A tibble of `ManyEcoEvo_yi_results`
 #' @param ManyEcoEvo A tibble of `ManyEcoEvo`

### 2023-11-15 R/summarise_sorensen_index.R

@@ -1,5 +1,9 @@
 #' Summarise Mean Sorensen's Index Estimates
-#'
+#' 
+#' @details
+#' Generates data summary with [summarise_sorensen_index_data()].
+#' 
+#' 
 #' @param ManyEcoEvo_results A tibble of `ManyEcoEvo_results`
 #' @param ManyEcoEvo_yi_results A tibble of `ManyEcoEvo_yi_results`
 #'

### 2023-11-15 R/summarise_variable_counts.R

@@ -1,7 +1,7 @@
 #' Summarise variable usage across analyses
 #' 
 #' @description
-#' Calculates either the counts of analyses in which each variable is used for a given dataset, or the mean, sd, minimum and maximum of those counts.
+#' Using [count_analyses_variables_used()] calculates the counts of analyses in which each variable is used for a given `dataset`. Further summarisation of those counts ( `mean`, `sd`, `min` and `max`) is optional, see details.
 #' 
 #' @details To calculate count values, supply `"count"` to argument `output`. To calculate summary statistics of counts, supply `"aggregate"` to argument `output` instead.
 #' 
@@ -10,7 +10,7 @@
 #' @param ManyEcoEvo A tibble of `ManyEcoEvo`
 #' @param output A length 1 character vector equal to `"count"` or `"aggregate"`
 #'
-#' @return A dataframe of count values `n` or summary statistic values `n_mean`/`n_sd`/`n_min`/`n_max` of counts depending on the the value supplied to the `output` argument. 
+#' @return A dataframe of count values `n` or summary statistic values `n_mean`,`n_sd`,`n_min`,`n_max` of counts depending on the the value supplied to the `output` argument. 
 #' @export
 #' @importFrom dplyr filter
 #' @importFrom dplyr select

### 2023-11-15 manuscript/manuscript/manuscript.Rmd
close #25 incorporate FF feedback

@@
 
+Many-analyst studies are a format of crowd-sourced scientific analysis [@schweinsberg2021], where analysts simultaneously, but independently, research the same research question, using the same dataset [@Voracek2019; @silberzahn2018].
+Many-analyst studies demonstrate how subjective, often arbitrary and usually defensible analysis decisions may influence research results [@silberzahn2018] due to either disagreement among researchers or due to analytic uncertainty about choices such as which observations to include and what data-analysis strategy is most appropriate [@Voracek2019].
+Managing the analysis pipeline of such data is complex and is better implemented with dedicated software.
+
 Typical scientific approaches proceed with a single team, and one analytic specification, or at most several specifications implemented.
@@
 Similarly, specification curve analysis of published findings have demonstrated that the published conclusion had empirical support from only a small sample of the overall plausible specifications (evidence of spurious findings, and possibly publication bias and p-hacking) [@Simonsohn2019].
+These types of studies are growing in popularity, as we explain below.
 
-Many-analyst studies are a format of crowd-sourced scientific analysis [@schweinsberg2021], where analysts simultaneously, but independently, research the same research question, using the same dataset [@Voracek2019; @silberzahn2018].
-Many-analyst studies demonstrate how subjective, often arbitrary and usually defensible analysis decisions may influence research results [@silberzahn2018] due to either disagreement among researchers or due to analytic uncertainty about choices such as which observations to include and what data-analysis strategy is most appropriate [@Voracek2019].
+*ManyEcoEvo* is an R package [@RCoreTeam2022] designed to *facilitate the analysis of* a many-analyst study in ecology and evolutionary biology, the *ManyEcoEvo Project* [@gould2023].
+The purpose of *ManyEcoEvo* is to reproducibly implement the analysis and presentation of results for Gould *et al.* [-@gould2023] such that the 246 analysts as well as other interested researchers may independently reproduce the study's findings.
+The package also aims to facilitate re-analyses and replications of Gould *et al.* [-@gould2023], as well as facilitating the analysis of similar many-analyst style datasets.
 
@@
 
-*ManyEcoEvo* is an R package [@RCoreTeam2022] designed to *facilitate the analysis of* a many-analyst study in ecology and evolutionary biology, the *ManyEcoEvo Project* [@gould2023].
-The purpose of *ManyEcoEvo* is to reproducibly implement the analysis and presentation of results for Gould *et al.* [-@gould2023] such that the 246 analysts as well as other interested researchers may independently reproduce the study's findings.
-The package also aims to facilitate re-analyses and replications of Gould *et al.* [-@gould2023], as well as facilitating the analysis of similar many-analyst style datasets.
-
-All raw data sets and metadata provided to independent teams for analysiss are publicly archived at <https://osf.io/qjzby> and <https://osf.io/hdv8m>, respectively.
+All raw data sets and metadata provided to independent teams for analysis are publicly archived at <https://osf.io/qjzby> and <https://osf.io/hdv8m>, respectively.
 Analyst survey responses and results are provided in the package GitHub repository (<https://github.com/egouldo/ManyEcoEvo/>), which is also archived on Zenodo (<https://doi.org/10.5281/zenodo.10046153>).
@@
 
+The last ten years has seen the growing emergence of many-analyst projects, [e.g.
+@silberzahn2018; @botvinik-nezer2020; @huntington-klein2021; @schweinsberg2021; @breznau2022; @hoogeveen2022many; @coretta2023], predominantly in the disciplines of psychology and social and behavioural sciences, however we expect more of these types of studies to be published into the near future across other disciplines.
+Moreover, collaborative and distributed big team open science projects are becoming increasingly common in ecology and evolutionary biology (e.g.
+NutNet/DragNet [nutnet.org/index.php/](https://nutnet.org/index.php/){.uri}, ManyBirds [themanybirds.com](http://themanybirds.com){.uri}) as well as other disciplines [ManyBabies @ManyBabies , ManyPrimates @ManyPrimates] which pose computationally analogous data-manipulation and analysis problems to the many-analyst workflow addressed by the *ManyEcoEvo* approach.
+
 The *ManyEcoEvo* package was created to implement the analysis for the 'Same Data, Many Analysts in Ecology and Evolutionary Biology' project [@gould2023] and to allow the 246 co-authors and other interested researchers to computationally reproduce our analysis.
 Following [@Marwick2018], [@Vuorre2021] and [@Filazzola2022], we opted to develop this research compendium as an R package as we find it best encapsulates the principles of 'clean code' for effective communication of the science, and therefore facilitates future reproduction, replication and potential synthesis [R packages as research compendia].
+*ManyEcoEvo* was designed for the ManyEcoEvo project, the structured approach it employs establishes a workflow that can be generalised and applied to new many-analyst style data, facilitating replication of Gould *et al.* [-@gould2023], in addition to computational reproduction [@Stoudt2021], as well as new analyses of many-analyst type studies.
+
 The results of some many-analyst studies have been controversial, yielding re-analyses criticising the original implementation of some many-analyst studies.
@@
 We also aim to facilitate analytic reproductions of this study, wherein *ManyEcoEvo* can be used to re-run the analysis in Gould *et al.* [-@gould2023] with slightly different methods, or subsets of data in order to verify and examine the robustness of our findings.
-
-The last ten years has seen the growing emergence of many-analyst projects, [e.g.
-@silberzahn2018; @botvinik-nezer2020; @huntington-klein2021; @schweinsberg2021; @breznau2022; @hoogeveen2022many; @coretta2023], predominantly in the disciplines of psychology and social and behavioural sciences, however we expect more of these types of studies to be published into the near future across other disciplines.
-Moreover, collaborative and distributed big team open science projects are becoming increasingly common in ecology and evolutionary biology (e.g.
-NutNet/DragNet <https://nutnet.org/index.php/>, ManyBirds <http://themanybirds.com>) as well as other disciplines [ManyBabies @ManyBabies , ManyPrimates @ManyPrimates] which pose computationally analogous data-manipulation and analysis problems to the many-analyst workflow addressed by the *ManyEcoEvo* approach.
-While *ManyEcoEvo* was designed for the ManyEcoEvo project, the structured approach it employs establishes a workflow that can be generalised and applied to new many-analyst style data, facilitating replication of Gould *et al.* [-@gould2023], in addition to computational reproduction [@Stoudt2021], as well as new analyses of many-analyst type studies.
 

### 2023-11-15 manuscript/manuscript/manuscript.Rmd
#25 rm italicisation on ManyEcoEvo project, except after first instance

@@
 
-The *ManyEcoEvo* project is a many-analyst study that aimed to empirically explore the variation in effect sizes and model predictions generated by analytical decisions of different researchers within ecology and evolutionary biology [@gould2023].
+The ManyEcoEvo project is a many-analyst study that aimed to empirically explore the variation in effect sizes and model predictions generated by analytical decisions of different researchers within ecology and evolutionary biology [@gould2023].
 174 analyst teams, comprising 246 analysts, independently investigated the answers to two pre-specified research questions using two previously unpublished datasets, one from conservation ecology, and one from evolutionary biology.

### 2024-05-24 README.qmd

@@
 
-# ManyEcoEvo <img src="man/figures/ManyEcoEvoHex.jpg" align="right" width="120"/>
+# ManyEcoEvo <img src="man/figures/logo.png" align="right" width="120"/>
 
@@
 1.  Clone or download [https://github.com/egouldo/this repository](https://github.com/egouldo/ManyEcoEvo)
-2.  Run `renv::restore()` to load the packages used in the analysis pipeline locally on your machine (see [`renv::`]https://rstudio.github.io/renv/index.html) for details)
+2.  Run `renv::restore()` to load the packages used in the analysis pipeline locally on your machine (see [`renv::`](https://rstudio.github.io/renv/index.html) for details)
 3.  Run `tar_destroy()` to remove any record and caches of existing targets

### 2024-08-05 R/standardise_response.R
#80 add further details on implicit exclusions

@@ -6,6 +6,9 @@
 #' @param dataset One of either "blue tit" or "eucalyptus"
 #'
 #' @return A tibble of analyst data with standardised values contained in a list-column called 'back_transformed_data'
+#' @details
+#' Note that for $y_i$ or out of sample predictions that are standardised, if param_table is `NA` or `NULL` for a given variable, then the response variable will not be standardised, and NA will be returned for that entry in `back_transformed_data`.
+#' 
 #' @export 
 #' @family analyst-data
 standardise_response <-  function(dat, 
@@ -78,6 +81,7 @@ standardise_response <-  function(dat,
                                   }else{NA}))
   }
   
+  #TODO for any analyses implicitly excluded, return a message to the user
   return(dat)
   
 }

### 2024-08-05 data-raw/analysis_datasets/osf_load_analyst_datasets.R
#80 tidy and organise package data generation script

@@ -1,15 +1,19 @@
-# Load Analyst Datasets from OSF - creates exported datasets: `euc_data` and `blue_tit_data`
+# Load Analyst Datasets from OSF - creates exported datasets: 
+# `euc_data` and `blue_tit_data`
 
 library(tidyverse)
-library(osfr) # Must have personal access token stored
 library(here)
+library(osfr) # Must have personal access token stored
+# to authenticate, follow these instructions: 
+# https://cran.r-project.org/web/packages/osfr/vignettes/auth.html
 
-#Download the Euc data from the OSF:
-osf_repo <- osfr::osf_retrieve_node("https://osf.io/mn5aj/") # to authenticate, follow these instructions: https://cran.r-project.org/web/packages/osfr/vignettes/auth.html
+# ----- Download analysis datasets from the OSF -----
+# 
+osf_repo <- osfr::osf_retrieve_node("https://osf.io/mn5aj/") 
 
 evo_eco_data_node <- osfr::osf_retrieve_node("34fzc")
 
-# Download Eucalyptus Data
+## ----- Download Eucalyptus Data -----
 
 osf_repo %>% 
   osfr::osf_ls_nodes() %>% 
@@ -21,10 +25,10 @@ osf_repo %>%
   dplyr::pull("id") %>% 
   osfr::osf_retrieve_file() %>% 
   osfr::osf_download(path = here::here("data-raw/analysis_datasets/"), 
-               progress = TRUE,
-               conflicts = "overwrite")
+                     progress = TRUE,
+                     conflicts = "overwrite")
 
-# Download Blue Tit Data
+## ----- Download Blue Tit Data -----
 osf_repo %>% 
   osfr::osf_ls_nodes() %>% 
   dplyr::filter(name == "Evolutionary Ecology Data") %>% 
@@ -35,23 +39,26 @@ osf_repo %>%
   dplyr::pull("id") %>% 
   osfr::osf_retrieve_file() %>% 
   osfr::osf_download(path = here::here("data-raw/analysis_datasets/"), 
-               progress = TRUE,
-               conflicts = "overwrite")
+                     progress = TRUE,
+                     conflicts = "overwrite")
 
-# Load Analyst Datasets
 
-euc_data <- readr::read_csv(here::here("data-raw/analysis_datasets/Euc_data.csv")) %>% 
[…]

### 2024-08-05 data-raw/analysis_datasets/README.qmd
#80 Add quarto markdown explaining package data generation
And explain implicit exclusions from yi meta-analysis

---
title: "README: `data-raw/analysis_datasets`"
format: gfm
---

This directory contains the analysis datasets used by analysis teams to answer the project's research questions.

-   `blue_tit_data_updated_2020-04-18.csv` contains the Evolutionary Ecology or Blue tit dataset, stored at <https://osf.io/34fzc/>.
-   `Euc_data.csv` contains the Ecology and Conservation or Eucalyptus dataset, stored at <https://osf.io/t76uy/>.

The two files are downloaded to this directory using the script `osf_load_analyst_datasets.R`, which uses the [`osfr::` package](https://github.com/ropensci/osfr).

For assistance with setting up authentication to run this script, check out <https://cran.r-project.org/web/packages/osfr/vignettes/auth.html>. Alternatively, simply download the files directly from the OSF using the URL's above. The script downloads the files, loads them into R, and then calculates some additional variables, which were variables constructed by analysts, but not present in the supplied analysis datasets.

This script creates the package data `euc_data` and `blue_tit_data`.

## A note on additional variable construction in `osf_load_analyst_datasets.R` and potential for implicit exclusion

Note that for inclusion in the out-of-sample predictions $y_i$ meta-analysis, parameter tables including the mean and SD for each response variable are needed standardise the data. If the variable is not present in either `euc_data` or `blue_tit_data` (i.e. it isn't calculated in `osf_load_analyst_datasets.R`, nor present in the original data files downloaded from the OSF), then analyses using that response variable are excluded from further meta-analysis. See table below for constructed variables that are included/excluded in the out-of-sample predictions meta-analysis:

```{R}
#| label: tbl-constructed-variables
#| results: asis
#| echo: true
#| message: false
#| code-fold: true

library(ManyEcoEvo)
library(dplyr)
library(purrr)
library(stringr)
library(tidyr)
library(tibble)

# Constructed Variables Included in the ManyAnalysts meta-analysis
ManyEcoEvo_constructed_vars <-
  tribble(~response_variable_name,
          "euc_sdlgs_all",
          "euc_sdlgs>50cm",
          "euc_sdlgs0_2m",
          "small*0.25+medium*1.25+large*2.5",
          "euc_sdlgs50cm_2m",
          "average.proportion.of.plots.containing.at.least.one.euc.seedling.of.any.size",
          "day_14_weight/(day_14_tarsus_length^2)",
          "day_14_weight/day_14_tarsus_length",
          "day_14_weight*day_14_tarsus_length"
  )

# Analyst Constructed Variables
all_constructed_vars <- 
  ManyEcoEvo %>% 
    pull(data, dataset) %>% 
    list_rbind(names_to = "dataset") %>% 
    filter(str_detect(response_variable_type, "constructed")) %>% 
    distinct(response_variable_name) %>% 
    drop_na() %>% 
    arrange()

by <- join_by(response_variable_name)

all_constructed_vars %>% 
  semi_join(ManyEcoEvo_constructed_vars, by) %>% 
  mutate(included_in_yi = TRUE) %>% 
  bind_rows(
    {
      all_constructed_vars %>% 
        anti_join(ManyEcoEvo_constructed_vars, by) %>% 
        mutate(included_in_yi = FALSE)
    }
  ) %>% 
  knitr::kable(col.names = c("Constructed Variable", 
                             "Included in $y_i$ meta-analysis?"), 
               format = "markdown")
```

### 2024-08-05 _targets.R
#80 add render data-raw/README in targets pipeline

@@ -242,6 +242,8 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                                                                               expertise_subset == "All",
                                                                               collinearity_subset == "All"))),
      tarchetypes::tar_quarto(name = README,
-                             path = "README.qmd")
+                             path = "README.qmd"),
+     tarchetypes::tar_quarto(name = README_data_raw,
+                             path = here::here("data-raw/analysis_datasets/", "README.qmd"))
      # tarchetypes::tar_quarto(full_analysis, "analysis/analysis_revised_data.qmd")
 )

### 2024-08-05 _targets.R
rm redundant code

@@ -245,5 +245,4 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                              path = "README.qmd"),
      tarchetypes::tar_quarto(name = README_data_raw,
                              path = here::here("data-raw/analysis_datasets/", "README.qmd"))
-     # tarchetypes::tar_quarto(full_analysis, "analysis/analysis_revised_data.qmd")
 )

### 2024-08-05 _targets.R
Add lme4 to targets #29 #67

@@ -21,8 +21,10 @@ pkgs <- c("tidyverse",
           "performance",
           "janitor",
           "rsvg",
+          "lme4",
           "multilevelmod",
           "metafor",
+          "parameters", # must be directly loaded else parameters::parameters() fails on lmerMod for some reason...
           "ManyEcoEvo") #TODO rm from here and just call in tar_option_set(), but will need to rm all namespacing
 
 tar_option_set(

### 2024-08-10 R/augment_prediction_data.R
#93 usethis::use_tidy_style()

@@ -1,15 +1,15 @@
 #' Augment analyst out-of-sample prediction data according to the outcome of pointblank interrogation
-#' @description 
-#' `augment_prediction_data()` will relabel and remove extraneous columns from 
+#' @description
+#' `augment_prediction_data()` will relabel and remove extraneous columns from
 #' out-of-sample prediction data.
-#' @details 
-#' Where there are missing variables in `.data` or `checks` is missing, 
+#' @details
+#' Where there are missing variables in `.data` or `checks` is missing,
 #' `NA` will be returned for the augmented prediction data instead.
 #' @param .data A data.frame of out of-sample-predictions analyst submission data
 #' @param checks A data.frame of pointblank interrogation output for `.data`
 #' @param dataset A character string equal to either "blue tit" or "eucalyptus"
 #'
-#' @return A dataframe. Individual analyst submission containing augmented 
+#' @return A dataframe. Individual analyst submission containing augmented
 #' out-of-sample prediction data ready for meta-analysis.
 #' @export
 #'

### 2024-08-10 R/fit_boxcox_ratings_ord.R

@@ -1,12 +1,12 @@
 #' Fit model of boxcox deviation scores as function of continuous ratings
-#' @description 
-#' Fit an lmer model of the box-cox transformed deviation from the meta-analytic 
+#' @description
+#' Fit an lmer model of the box-cox transformed deviation from the meta-analytic
 #' mean scores as a function of continuous peer-review ratings
 #'
 #' @param .data Data for model fitting
 #' @param outcome outcome variable, unquoted.
 #' @param outcome_var Variance of the `outcome` variable
-#' @param interceptless A logical relating to whether the model should be 
+#' @param interceptless A logical relating to whether the model should be
 #' interceptless or not. Defaults to `FALSE`.
 #'
 #' @return An object of class lmer.

### 2024-08-10 data-raw/analysis_datasets/osf_load_analyst_datasets.R

@@ -96,7 +96,7 @@ euc_data <- euc_data %>%
 blue_tit_data <-
   blue_tit_data %>%
   mutate(
-    `day 14 weight` = day_14_weight, 
+    `day 14 weight` = day_14_weight,
     `day_14_weight/(day_14_tarsus_length^2)` =
       day_14_weight / (day_14_tarsus_length^2),
     `day_14_weight/day_14_tarsus_length` =

### 2024-08-10 data-raw/metadata_and_key_data/round_1_question_key.R

@@ -96,10 +96,10 @@ covariates_key <-
   ) %>%
     paste(
       str_split(variable_name, "_") %>%
-        flatten_chr() %>% 
-        pluck(2), 
-      sep = "_")
-  )
+        flatten_chr() %>%
+        pluck(2),
+      sep = "_"
+    ))
 
 q_text <- process_survey_questions_r1("SV_8FU0Y2y0TaFLQXP") %>%
   filter(qname %in% c("Q37", "Q38")) %>%

### 2024-08-10 data-raw/analysis_datasets/README.qmd

@@
 library(tibble)
+data("ManyEcoEvo")
 
@@
 ManyEcoEvo_constructed_vars <-
-  tribble(~response_variable_name,
+  tribble(
+    ~response_variable_name,
     "euc_sdlgs_all",
@@
   mutate(included_in_yi = TRUE) %>%
-  bind_rows(
-    {
+  bind_rows({
     all_constructed_vars %>%
@@
       mutate(included_in_yi = FALSE)
-    }
-  ) %>% 
-  knitr::kable(col.names = c("Constructed Variable", 
-                             "Included in $y_i$ meta-analysis?"), 
-               format = "markdown")
+  }) %>%
+  knitr::kable(
+    col.names = c(
+      "Constructed Variable",
+      "Included in $y_i$ meta-analysis?"
+    ),
+    format = "markdown"
+  )
 ```

### 2024-08-10 R/clean_response_transformation.R
fix #76 move transformation_tbl to internally exported pkg object

@@ -1,34 +1,22 @@
 #' Clean response transformation variable
 #' @description Cleans the response transformation variable to the names of the back-transformation functions
 #'
-#' @param response_transformation A character vector with the
+#' @param response_transformation A character vector with the response transformation values
+#' @param transformation_tbl A tibble of the response transformation values `transformation_orig` and their cleaned names `cleaned_transformation`
+#' 
 #'
 #' @return A character vector of cleaned response transformation values equal to the required `transformation` values in `conversion()`
 #' @export
-#'
+#' @details
+#' The `transformation_tbl` is a tibble of the response transformation values `transformation_orig` and their cleaned
+#' names `cleaned_transformation`. The `transformation_orig` values are the original response transformation values
+#' used by the analyst. The `cleaned_transformation` values are the cleaned response transformation values that are equal to the required `transformation` values in [conversion()]. 
+#' The user can supply an alternate table of transformations depending on what is required for the back-transformation functions.
 #' @family back-transformation functions
-clean_response_transformation <- function(response_transformation) {
+clean_response_transformation <- function(response_transformation, 
+                                          transformation_tbl = ManyEcoEvo:::transformation_tbl) {
   original_data <- tibble(transformation_orig = response_transformation)
-
-  transformation_tbl <- tribble(
-    ~transformation_orig, ~cleaned_transformation,
-    "^2", "square",
-    "power2", "square",
-    "^3", "cube",
-    "power3", "cube",
-    "squared", "square",
-    "cubed", "cube",
-    "scaled and centered", "identity",
-    "scaling and centering", "identity",
-    "mean centered and standardized", "identity",
-    "log", "log",
-    "orderNorm", NA, # TODO, ensure that this is the best behaviour - we need to exclude this first, rather than let it through here.. because else it gets passed through identity_back() inside conversion()
-    "divided.by.14", "divided.by.14",
-    "square.root", "square_root",
-    "back.transformed", "back.transformed",
-    "z.score", "identity",
-    "(power3)/100", "(power3)/100"
-  ) # TODO double-check treatment of z.score
+  
   out <- original_data %>%
     left_join(transformation_tbl) %>%
     select(cleaned_transformation) %>% # TODO WHAT ABOUT MISSING NON-STANDARD TRANSFORMATIONS??

### 2024-08-10 data-raw/create_internal_pkg_data.R

@@ -366,6 +366,28 @@ prediction_ids <- tibble::tribble(
   "Cessnock-1-1-1"
 ) # TODO ask HF where/how derived (used data pasta to copy from HF's files)
 
+# ------ Create transformation_tbl -----
+
+transformation_tbl <- tribble(
+  ~transformation_orig, ~cleaned_transformation,
+  "^2", "square",
+  "power2", "square",
+  "^3", "cube",
+  "power3", "cube",
+  "squared", "square",
+  "cubed", "cube",
+  "scaled and centered", "identity",
+  "scaling and centering", "identity",
+  "mean centered and standardized", "identity",
+  "log", "log",
+  "orderNorm", NA, # TODO, ensure that this is the best behaviour - we need to exclude this first, rather than let it through here.. because else it gets passed through identity_back() inside conversion()
+  "divided.by.14", "divided.by.14",
+  "square.root", "square_root",
+  "back.transformed", "back.transformed",
+  "z.score", "identity",
+  "(power3)/100", "(power3)/100"
+) 
+
 
 # ------- Write data internally -------
 
@@ -374,6 +396,7 @@ usethis::use_data(expert_subset,
   collinearity_subset,
   prediction_ids,
   effect_ids,
+  transformation_tbl,
   internal = TRUE,
   overwrite = TRUE
 )

### 2024-08-11 R/compute_MA_inputs.R
My Signed Commit
Signed-off-by: egouldo <egouldo@users.noreply.github.com>

@@ -2,7 +2,7 @@
 #' @description Computes the sorensen diversity indices and joins it to the prepared data in preparation for meta-analysing all subsets of data with `meta_analyse_datasets()`.
 #'
 #' @param ManyEcoEvo A dataframe grouped by the character columns `dataset`, `estimate_type`, `exclusion_set`. Each group corresponds to a subset of the full `dataset`, and has the subset analyst data  stored in `data`, with its corresponding subset `diversity_data`.
-#' @param estimate_type
+#' @param estimate_type character string, one of "Zr", "yi", "y25", "y50", "y75".
 #' @details The name of the subset is derived from the funs generated by `subset_fns_yi` and/or `subset_fns_Zr`.
 #'
 #' Computes sorensen diversity indices `diversity_indices` for each subset of data returning them in the list-columns `diversity_indices` and joins them to the subset analyst `data`, returning it in the list-column `effects_analysis`.

### 2024-08-11 R/exclude_extreme_VZ.R

@@ -1,6 +1,6 @@
 #' Exclude extreme values of VZ from a dataframe of standardised predictions
 #'
-#' @param df
+#' @param df A dataframe containing the columns `Z` and `VZ`
 #' @param VZ_cutoff A numeric vector of length 1, values equal to or greater than this value of VZ will be filtered out of `df`.
 #'
 #' @return A dataframe with observations removed where the value is less than that of `VZ\_cutoff`.

### 2024-08-11 R/get_diversity_data.R

@@ -1,6 +1,6 @@
 #' Get Diversity Data
 #'
-#' @param raw_data
+#' @param raw_data A tibble of raw data
 #' @param dataset character string of either "eucalyptus" or "blue tit"
 #' @param variables character vector of any length containing names of variables to get diversity data for
 #'

### 2024-08-11 R/prepare_response_variables_yi.R

@@ -41,7 +41,7 @@ prepare_response_variables_yi <- function(ManyEcoEvo,
 
 #' Back Transform Response Variables - yi
 #'
-#' @param data
+#' @param dat A dataframe of out of sample predictions analyst submission data
 #' @param estimate_type The type of estimate to be standardised. Character vector of length 1, whose value may be  "yi", "y25", "y50", "y75".
 #' @param param_table A table of estimated 'population' parameters for each variable in the analysis datasets.
 #' @param dataset One of either "blue tit" or "eucalyptus"

### 2024-08-11 R/standardise_response.R

@@ -1,6 +1,6 @@
 #' Standardise Response Variable
 #'
-#' @param data
+#' @param dat A tibble of analyst data with a list-column called 
 #' @param estimate_type The type of estimate to be standardised. Character vector of length 1, whose value may be "Zr", "yi", "y25", "y50", "y75".
 #' @param param_table A table of estimated 'population' parameters for each variable in the analysis datasets.
 #' @param dataset One of either "blue tit" or "eucalyptus"

### 2024-08-11 R/utils.R

@@ -81,9 +81,9 @@ capwords <- function(s, strict = FALSE) {
 
 #' Removes infinite and NA values from a dataframe of standardised effects
 #'
-#' @param effects_analysis
 #' @param Z_colname unquoted or bare column name with the Z or Zr estimates
 #' @param VZ_colname unquoted or bare column name containing the VZ or VZr estimates
+#' @param effects_analysis A dataframe containing the standardised effects
 #'
 #' @return a dataframe without
 #' @export

### 2024-08-11 R/utils.R
#102 update roxygen examples and doc /document

@@ -1,8 +1,9 @@
 #' Negative Value Matching
 #'
-#' See \code{base::[](`%in%`)} for details. %nin% is a binary operator, returning a logical vector indicating if there is a negative match or not.
+#' See \code{base::[](`%in%`)} for details. `%nin%` is a binary operator, 
+#' returning a logical vector indicating if there is a negative match or not.
 #'
-#' @name %in%
+#' @name %nin%
 #' @rdname NotIn
 #' @keywords internal
 #' @export
@@ -10,13 +11,14 @@
 #' @param lhs vector or NULL: the values to be matched. [Long vectors](http://127.0.0.1:59782/help/library/base/help/Long%20vectors) are supported.
 #' @param rhs vector or NULL: the values to be matched. [Long vectors](http://127.0.0.1:59782/help/library/base/help/Long%20vectors) are supported.
 #' @return A logical vector indicating which value of `lhs` are *not* matched in `rhs`
+#' @examples
+#' "A" %nin% LETTERS[1:10]
+#' "A" %in% LETTERS[1:10]
 `%nin%` <- Negate(`%in%`)
 
-
-
-#' Subsetting Functions for Zr analysis
+#' Subsetting Functions for effect-size meta-analysis
 #'
-#' @description Generates a list of functions that are used to subset the processed ManyEcoEvo dataset
+#' @description Generates a list of functions that are used to subset the processed [ManyEcoEvo::] dataset
 #'
 #' @return A named list of `lambda` functions
 #' @export
@@ -38,9 +40,15 @@ subset_fns_Zr <- function() { # TODO update calling of this fn (switch to fn rat
   return(out)
 }
 
-#' Subsetting Functions for yi analysis
+#' Subsetting Functions for out-of-sample predictions meta-analysis
 #'
-#' @description Generates a list of functions that are used to subset the processed ManyEcoEvo dataset containing out-of-sample predictions \(\code{y\_i}\)
+#' @description Generates a list of functions that are used to subset the 
+#' processed ManyEcoEvo dataset (e.g.`data(ManyEcoEvo_results`) containing 
+#' out-of-sample predictions $y_i$. 
+#' 
+#' @details 
+#' The subset functions are used to filter out predictions that are not 
+#' to be included in the meta-analysis.
 #'
 #' @return A named list of `lambda` functions
 #' @export
[…]

### 2024-08-11 R/clean_response_transformation.R
#102 add examples, seealso and explicit `by = ` argument in `left_join()` call

@@ -13,12 +13,17 @@
 #' used by the analyst. The `cleaned_transformation` values are the cleaned response transformation values that are equal to the required `transformation` values in [conversion()]. 
 #' The user can supply an alternate table of transformations depending on what is required for the back-transformation functions.
 #' @family back-transformation functions
+#' @seealso To be called after to [assign_transformation_type()]
+#' @examples
+#' clean_response_transformation("power2", ManyEcoEvo:::transformation_tbl) 
+#' clean_response_transformation("log", ManyEcoEvo:::transformation_tbl)
+#' clean_response_transformation("new_transformation", ManyEcoEvo:::transformation_tbl ) # Returns NA if not found
 clean_response_transformation <- function(response_transformation, 
                                           transformation_tbl = ManyEcoEvo:::transformation_tbl) {
   original_data <- tibble(transformation_orig = response_transformation)
   
   out <- original_data %>%
-    left_join(transformation_tbl) %>%
+    left_join(transformation_tbl, by = join_by(transformation_orig)) %>%
     select(cleaned_transformation) %>% # TODO WHAT ABOUT MISSING NON-STANDARD TRANSFORMATIONS??
     flatten_chr()
 

### 2024-08-11 R/assign_transformation_type.R
#102 update function roxygen - rename fn title, - give more detail in `@returns`, - explain mechanics in `@details`, - switch to `@import` instead of `@importFrom`, - add `@family` and `@seealso tags`

@@ -1,13 +1,16 @@
-#' Assign back-transformation type to be applied to analysis point-estimates
+#' Assign back-transformation type to be applied to analysts' point-estimates
 #'
 #' @param response_transformation Character vector of length 1L containing the analysis response transformation
 #' @param link_fun Character vector of length 1L containing the analysis link function
 #'
-#' @return A character vector of length 1L
+#' @return A character vector of length 1L containing the back-transformation type to be applied to the analysts' point-estimates. Is either "identity", "double_transformation", or the value of `link_fun` or `response_transformation`, or `NA`, if an appropriate transformation type cannot be assigned.
+#' @details 
+#' Based on the response transformation and link function, the function assigns the back-transformation type to be applied to the analysts' point-estimates. The function and assigns the identity transformation if the effects were reported on the link-scale and the estimates are already back-transformed the original response variable prior to modelling. When either of these cases is not true for a given analysis, the function returns the value of the `link_fun` or `response_transformation` argument. When an analysis has been reported on the link-scale and the analyst transformed the response variable prior to modelling, the function assigns the `"double-transformation"`  value for that analysis. When the `response_transformation` and `link_fun` arguments are missing, the function assigns the `"identity"` value to the analysis, assuming that `NA` values are equivalent to the identity transformation. 
 #' @export
-#' @importFrom dplyr case_when
-#' @importFrom rlang is_na
-#' @importFrom rlang na_chr
+#' @import dplyr
+#' @import rlang
+#' @family back-transformation functions
+#' @seealso [prepare_response_variables_yi(), standardise_response()]. To be called prior to [clean_response_transformation()].
 assign_transformation_type <- function(response_transformation = character(1L),
                                        link_fun = character(1L)) {
   # # Link-Fun: Set back.transformed to "identity"

### 2024-08-11 R/standardise_response.R

@@ -7,6 +7,14 @@
 #'
 #' @return A tibble of analyst data with standardised values contained in a list-column called 'back_transformed_data'
 #' @details
+#' 
+#' When the `estimate_type` is `"Zr"`, [standardise_response()] standardises effect-sizes with [est_to_zr()], assuming that the `beta_estimate` and `beta_SE` values have already been back-transformed to the appropriate scale. #TODO check this.
+#' 
+#' When the `estimate-type` is `"yi"` or otherwise, the function:
+#' 1. assigns a `transformation_type` with [assign_transformation_type()]
+#' 2. Converts the out-of-sample predictions on the link- or transformed-response scale back to the original response scale using [convert_predictions()].
+#' 3. Standardises predictions on the original response-scale to the Z-scale, with [pred_to_Z()].
+#' 
 #' Note that for $y_i$ or out of sample predictions that are standardised, if param_table is `NA` or `NULL` for a given variable, then the response variable will not be standardised, and NA will be returned for that entry in `back_transformed_data`.
 #'
 #' @export
@@ -20,7 +28,7 @@ standardise_response <- function(dat,
   match.arg(estimate_type, choices = c("Zr", "yi", "y25", "y50", "y75"), several.ok = FALSE)
   match.arg(dataset, choices = c("eucalyptus", "blue tit"), several.ok = FALSE)
   cli::cli_h1(glue::glue("Computing meta-analysis inputs", "for estimate type ", "{estimate_type}"))
-
+  
   if (estimate_type == "Zr") {
     # Convert Effect Sizes to Zr -------
     cli::cli_h2(paste0("Computing standardised effect sizes ", "{.code Zr}", " and variance ", "{.code VZr}"))
@@ -56,20 +64,23 @@ standardise_response <- function(dat,
         analysis_id,
         split_id
       ) %>%
-      dplyr::mutate(params = purrr::map(
-        .x = response_variable_name,
-        .y = param_table,
-        .f = ~ dplyr::filter(.y, variable == .x)
-      )) %>%
-      dplyr::mutate(nrow_params = purrr::map_int(params, nrow)) %>%
-      dplyr::mutate(params = purrr::map2(params,
-        nrow_params,
-        .f = ~ if (.y > 0) {
-          .x
-        } else {
-          NA
-        }
-      )) %>%
+      dplyr::mutate(params = 
+                      purrr::map(
+                        .x = response_variable_name,
+                        .y = param_table,
+                        .f = ~ dplyr::filter(.y, variable == .x)
+                      )) %>%
[…]

### 2024-08-11 R/utils.R

@@ -89,7 +89,7 @@ capwords <- function(s, strict = FALSE) {
 #'
 #' @param effects_analysis A dataframe containing the standardised effects
 #' @param Z_colname unquoted or bare column name with the $Z$ or $Z_r$ estimates
-#' @param VZ_colname unquoted or bare column name containing the $VZ$ or $\text{VZ}_r$ estimates
+#' @param VZ_colname unquoted or bare column name containing the $VZ$ or $\\text{VZ}_r$ estimates
 #'
 #' @return a dataframe without
 #' @export

### 2024-08-11 R/back_transformations.R
#102 combine @rdname and @describeIn approach to merging function documentation for `_back()` family \document

@@ -1,17 +1,21 @@
 # --- Back-transformation Conversion Functions ---
-# convertion functions
-# we assume estimates are normally distributed
-# TODO Question - all natural log (no log10)
-
-#' Back transform beta estimates for models with log-link
-#'
-#' @param beta Analyst beta estimate or yi estimate
-#' @param se Standard error of analyst's beta estimate or yi estimate.
+#' Back-transform effect-sizes to response scale.
+#' @description
+#' Transforms effect-sizes and their standard errors to the response scale.
+#' 
+#' @details We assume analysts' estimates are normally distributed. Each function uses a normal distribution to simulate the a distribution of effect-sizes and their standard errors. Next this distribution is back-transformed to the desired response scale. The mean `m_est`, standard error `se_est`, and quantiles (`lower` and `upper`) of the back-transformed distribution are returned within a dataframe.
+#' @param beta Analyst beta estimate
+#' @param se Standard error of analyst's effect size estimate $\\beta$ 
+#' or out-of-sample prediction estimate $y\\_i$.
 #' @param sim numeric vector of length 1. number of simulations.
-#'
-#' @return data frame containing the mean estimate, its standard error, and quantiles
-#' @export
+#' @return data frame containing the mean estimate, its standard error, and quantiles.
 #' @family back transformation
+#' @name back
+NULL
+#> NULL
+
+#' @describeIn back Back transform beta estimates for models with log-link
+#' @export
 log_back <- function(beta, se, sim) {
   simulated <- rnorm(sim, beta, se)
   original <- exp(simulated) %>% # exponential = inverse of log
@@ -29,14 +33,8 @@ log_back <- function(beta, se, sim) {
   return(set)
 }
 
-#' Back transform beta estimates for models with logit-link
-#' @param beta Analyst beta estimate
-#' @param se Standard error of analyst's beta estimate.
-#' @param sim numeric vector of length 1. number of simulations.
-#'
-#' @return data frame containing the mean estimate, its standard error, and quantiles
+#' @describeIn back Back transform beta estimates for models with logit-link
 #' @export
-#' @family back transformation
 logit_back <- function(beta, se, sim) {
   simulated <- rnorm(sim, beta, se)
   original <- plogis(simulated) %>% # invlogit
@@ -54,14 +52,8 @@ logit_back <- function(beta, se, sim) {
   return(set)
 }
 
-#' Back transform beta estimates for models with probit-link
[…]

### 2024-08-11 R/convert_predictions.R
#102 add `@import` calls to function doc

@@ -4,6 +4,12 @@
 #' @return A tibble of out of sample predictions on the response variable scale of the response variable used by the analyst
 #' @family analysis-values
 #' @export
+#' @import dplyr
+#' @import purrr
+#' @import rlang
+#' @import cli
+#' @importFrom data.table setnames
+#' @importFrom pointblank has_columns
 convert_predictions <- function(augmented_data,
                                 transformation_type,
                                 response_transformation,
@@ -92,7 +98,6 @@ convert_predictions <- function(augmented_data,
         cli::cli_alert_warning("Missing Value for {.arg response_transformation}, returning {.val NA}")
         out <- rlang::na_cpl
       }
-
 
       vconvert_double_transformation(
         beta = beta_vals,

### 2024-08-11 R/standardise_response.R
#102 add `@seealso` entry

@@ -11,7 +11,7 @@
 #' When the `estimate_type` is `"Zr"`, [standardise_response()] standardises effect-sizes with [est_to_zr()], assuming that the `beta_estimate` and `beta_SE` values have already been back-transformed to the appropriate scale. #TODO check this.
 #' 
 #' When the `estimate-type` is `"yi"` or otherwise, the function:
-#' 1. assigns a `transformation_type` with [assign_transformation_type()]
+#' 1. assigns a `transformation_type` with [assign_transformation_type()], assumes that 
 #' 2. Converts the out-of-sample predictions on the link- or transformed-response scale back to the original response scale using [convert_predictions()].
 #' 3. Standardises predictions on the original response-scale to the Z-scale, with [pred_to_Z()].
 #' 
@@ -19,6 +19,7 @@
 #'
 #' @export
 #' @family analyst-data
+#' @seealso [est_to_zr(), assign_transformation_type()]
 standardise_response <- function(dat,
                                  estimate_type = character(1L),
                                  param_table = NULL,

### 2024-08-12 R/compute_metaanalysis_inputs.R
Typo in cli output

@@ -8,7 +8,7 @@
 compute_metaanalysis_inputs <- function(.data, estimate_type = character(1L)) {
   # TODO insert checks that appropriate columns exist
   match.arg(estimate_type, choices = c("Zr", "yi", "y25", "y50", "y75"), several.ok = FALSE)
-  cli::cli_h1(glue::glue("Computing meta-analysis inputs", "for estimate type ", "{estimate_type}"))
+  cli::cli_h1(glue::glue("Computing meta-analysis inputs", " for estimate type ", "{estimate_type}"))
 
   if (estimate_type == "Zr") {
     # Convert Effect Sizes to Zr -------

### 2024-08-12 R/utils.R
#102 update and add `@import` calls

@@ -52,6 +52,8 @@ subset_fns_Zr <- function() { # TODO update calling of this fn (switch to fn rat
 #'
 #' @return A named list of `lambda` functions
 #' @export
+#' @import rlang
+#' @import dplyr
 subset_fns_yi <- function() {
   out <- list( # TODO: which dataset and variable are the prediction exclusions contained??
     subset_complete = rlang::as_function(~ .x %>%
@@ -94,6 +96,7 @@ capwords <- function(s, strict = FALSE) {
 #' @return a dataframe without
 #' @export
 #' @examples
+#' @import dplyr
 #' data(ManyEcoEvo_results)
 #' ManyEcoEvo_results %>% 
 #' pluck("effects_analysis", 1) %>% 
@@ -117,7 +120,9 @@ rm_inf_na <- function(effects_analysis, Z_colname, VZ_colname) {
 #'
 #' @return A named list of tibbles. Each tibble contains the rows of .tbl for the associated group and all the columns, including the grouping variables. Note that this returns a list_of which is slightly stricter than a simple list but is useful for representing lists where every element has the same type.
 #' @export
-#' @importFrom dplyr group_split
+#' @import dplyr
+#' @import rlang
+#' @import purrr
 #' @examples
 #' data(euc_data)
 #' data(blue_tit_data)

### 2024-08-12 R/compute_metaanalysis_inputs.R
add comment noting bug

@@ -40,13 +40,13 @@ compute_metaanalysis_inputs <- function(.data, estimate_type = character(1L)) {
       mutate(
         back_transformed_data =
           pmap(
-            .l = list(
+            .l = list( #TODO bug, missing argument
               augmented_data,
               link_function,
               response_transformation_description
             ),
             .f = ~ if (!rlang::is_na(..1) | !rlang::is_na(..2)) {
-              convert_predictions(
+              convert_predictions( #TODO bug, missing argument
                 augmented_data = ..1,
                 link_fun = ..2,
                 response_transformation = ..3

### 2024-08-12 R/utils.R
#97 #102 move `@examples` tag to correct line /document

@@ -95,8 +95,8 @@ capwords <- function(s, strict = FALSE) {
 #'
 #' @return a dataframe without
 #' @export
-#' @examples
 #' @import dplyr
+#' @examples
 #' data(ManyEcoEvo_results)
 #' ManyEcoEvo_results %>% 
 #' pluck("effects_analysis", 1) %>% 

### 2024-08-12 R/summarise_analysis_types.R
#102 #97 replace `@importFrom` calls with `@import`

@@ -12,22 +12,11 @@
 #'
 #' @return A summarised tibble with the variables `subset`, `dataset`, `num_teams`, `total_analyses`, `sum_linear`, `sum_mixed`, `sum_Bayesian`.
 #' @export
-#' @importFrom dplyr filter
-#' @importFrom dplyr select
-#' @importFrom dplyr group_by
-#' @importFrom dplyr rename
-#' @importFrom purrr map
-#' @importFrom broom tidy
-#' @importFrom tidyr unnest
-#' @importFrom magrittr "%>%"
-#' @importFrom dplyr distinct
-#' @importFrom dplyr mutate
+#' @import dplyr
+#' @import broom
+#' @import tidyr
 #' @import metafor
-#' @importFrom dplyr across
-#' @importFrom dplyr left_join
-#' @importFrom dplyr right_join
-#' @importFrom dplyr full_join
-#' @importFrom purrr map_dfr
+#' @import purrr
 #' @family Multi-dataset Wrapper Functions
 #' @author Hannah S. Fraser
 #' @author Elliot Gould
@@ -128,10 +117,7 @@ summarise_analysis_types <- function(ManyEcoEvo_results, ManyEcoEvo_yi_results, 
 #'
 #' @return A dataframe with the columns  `dataset`, `total_teams` and `total_analyses` equal in number of rows to the number of unique values within the `dataset` variable of the input `data`.
 #' @export
-#' @importFrom dplyr count
-#' @importFrom dplyr group_by
-#' @importFrom dplyr summarise
-#' @importFrom magrittr "%>%"
+#' @import dplyr
 #' @author Hannah S. Fraser
 #' @author Elliot Gould
 #' @examples
@@ -157,9 +143,7 @@ count_teams_analyses <- function(data) {
 #'
 #' @return A dataframe with the variables
 #' @export
-#' @importFrom dplyr group_by
-#' @importFrom dplyr summarise
-#' @importFrom magrittr "%>%"
+#' @import dplyr
 #' @author Hannah S. Fraser
 #' @author Elliot Gould
 #' @examples

### 2024-08-12 R/summarise_model_composition.R

@@ -12,19 +12,9 @@
 #'
 #' @return A dataframe
 #' @export
-#' @importFrom dplyr filter
-#' @importFrom dplyr select
-#' @importFrom tidyr unnest
-#' @importFrom dplyr mutate
-#' @importFrom dplyr rename
-#' @importFrom dplyr group_by
-#' @importFrom dplyr distinct
-#' @importFrom magrittr "%>%"
-#' @importFrom dplyr right_join
-#' @importFrom dplyr across
-#' @importFrom tidyr pivot_longer
-#' @importFrom purrr map_dfr
-#' @importFrom purrr set_names
+#' @import dplyr
+#' @import tidyr
+#' @import purrr
 #' @author Hannah S. Fraser
 #' @author Elliot Gould
 #' @family Multi-dataset Wrapper Functions

### 2024-08-12 R/summarise_sorensen_index.R

@@ -9,19 +9,9 @@
 #'
 #' @return A tibble of aggregate summary statistics (`mean`, `sd`, `min`, `max`) for mean Sorensen's index estimates across each `subset` and `dataset`.
 #' @export
-#' @importFrom dplyr filter
-#' @importFrom dplyr select
-#' @importFrom tidyr unnest
-#' @importFrom dplyr mutate
-#' @importFrom dplyr rename
-#' @importFrom dplyr group_by
-#' @importFrom dplyr distinct
-#' @importFrom magrittr "%>%"
-#' @importFrom dplyr right_join
-#' @importFrom dplyr across
-#' @importFrom tidyr pivot_longer
-#' @importFrom purrr map_dfr
-#' @importFrom purrr set_names
+#' @import dplyr
+#' @import tidyr
+#' @import purrr
 #' @author Hannah S. Fraser
 #' @author Elliot Gould
 #' @family Multi-dataset Wrapper Functions

### 2024-08-12 R/back_transformations.R
#102 #97 replace md equation syntax with roxygen

@@ -5,8 +5,8 @@
 #' 
 #' @details We assume analysts' estimates are normally distributed. Each function uses a normal distribution to simulate the a distribution of effect-sizes and their standard errors. Next this distribution is back-transformed to the desired response scale. The mean `m_est`, standard error `se_est`, and quantiles (`lower` and `upper`) of the back-transformed distribution are returned within a dataframe.
 #' @param beta Analyst beta estimate
-#' @param se Standard error of analyst's effect size estimate $\\beta$ 
-#' or out-of-sample prediction estimate $y\\_i$.
+#' @param se Standard error of analyst's effect size estimate \eqn{\beta} 
+#' or out-of-sample prediction estimate \eqn{y_i}.
 #' @param sim numeric vector of length 1. number of simulations.
 #' @return data frame containing the mean estimate, its standard error, and quantiles.
 #' @family back transformation
@@ -71,7 +71,7 @@ probit_back <- function(beta, se, sim) {
   return(set)
 }
 
-#' @describeIn back Back transform beta estimates for models with $1/x$ link
+#' @describeIn back Back transform beta estimates for models with \eqn{1/x} link
 #' @export
 inverse_back <- function(beta, se, sim) {
   simulated <- rnorm(sim, beta, se)
@@ -90,7 +90,7 @@ inverse_back <- function(beta, se, sim) {
   return(set)
 }
 
-#' @describeIn back Back transform beta estimates for models with $x^2$-link
+#' @describeIn back Back transform beta estimates for models with \eqn{x^2}-link
 #' @export
 square_back <- function(beta, se, sim) {
   simulated <- rnorm(sim, beta, se)
@@ -109,7 +109,7 @@ square_back <- function(beta, se, sim) {
   return(set)
 }
 
-#' @describeIn back Back transform beta estimates for models with $x^3$-link
+#' @describeIn back Back transform beta estimates for models with \eqn{x^3}-link
 #' @export
 cube_back <- function(beta, se, sim) {
   simulated <- rnorm(sim, beta, se)

### 2024-08-12 R/utils.R

@@ -90,8 +90,8 @@ capwords <- function(s, strict = FALSE) {
 #' Removes infinite and NA values from a dataframe of standardised effects
 #'
 #' @param effects_analysis A dataframe containing the standardised effects
-#' @param Z_colname unquoted or bare column name with the $Z$ or $Z_r$ estimates
-#' @param VZ_colname unquoted or bare column name containing the $VZ$ or $\\text{VZ}_r$ estimates
+#' @param Z_colname unquoted or bare column name with the \eqn{Z} or \eqn{Z_r} estimates
+#' @param VZ_colname unquoted or bare column name containing the \eqn{VZ} or \eqn{\text{VZ}_r} estimates
 #'
 #' @return a dataframe without
 #' @export

### 2024-08-14 _targets.R
close #88 update function call to `prepare_response_variables()` in targets - only standardise blue tit yi #88

@@ -242,7 +242,8 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                                                                                           "constructed", 
                                                                                           negate = TRUE)))) %>% 
                            prepare_response_variables(estimate_type = "yi",
-                                                                  param_table = ManyEcoEvo:::analysis_data_param_tables,dataset_standardise = "blue tit") %>%
+                                                      param_table = ManyEcoEvo:::analysis_data_param_tables, 
+                                                      dataset_standardise = "blue tit") %>%
                            generate_yi_subsets() %>% #TODO: must be run after prepare_response_variables??
                            apply_VZ_exclusions(3) %>%
                            generate_exclusion_subsets() %>% #TODO: runs on ManyEcoEvo that contains Zr and yi results.

### 2024-08-14 _targets.R
#97 linelength linting

@@ -124,23 +124,30 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                            ungroup() %>% 
                            mutate(
                              no_updated_checks = map_lgl(updated_checks, is_null),
-                             checks = ifelse(no_updated_checks == TRUE, checks, updated_checks),
+                             checks = ifelse(no_updated_checks == TRUE, 
+                                             checks, 
+                                             updated_checks),
                              .keep = "unused") %>% 
                            rowwise() %>% #NOTE: file_name and file_path replacement errors fails without rowwise
                            mutate(
-                             file_name = case_when(rlang::is_na(`new_csv_file_name--file-submissionID-csv_number`) ~ file_name,
-                                                   TRUE ~ `new_csv_file_name--file-submissionID-csv_number`),
-                             filepath = case_when(rlang::is_na(`new_csv_file_name--file-submissionID-csv_number`) ~ filepath, 
-                                                  TRUE ~ here::here("data-raw/analyst_data/S2", file_name)),
-                             exclude_read = case_when(response_id == "R_3dYDpQUfDUXjtDy" & submission_id == 2 ~ "exclude", # see col other_action & misc_notes in predictions_validation_worksheet.csv for reasons
-                                                      response_id == "R_3mfyhAj6rakbi5b" & submission_id == 1 ~ "exclude", #TODO: check whether THP's file has addressed these issues, if so we can remove this code as it is redundant
-                                                      response_id == "R_1BWpZlSbkmSofe1" & submission_id == 1 ~ "exclude",
-                                                      response_id == "R_1d0uRf5iNWOLD8M" & submission_id == 1 ~ "exclude",
-                                                      response_id == "R_3NHVKFiOiQBfX9b" & submission_id == 1 ~ "exclude",
-                                                      response_id == "R_3NHVKFiOiQBfX9b" & submission_id == 3 ~ "exclude",
-                                                      response_id == "R_1LRqq2WHrQaENtM" & submission_id == 1 ~ "exclude",
-                                                      response_id == "R_2V7qaLEfdbgUGg3" & submission_id == 1 ~ "exclude", # missing se.fit, but should be filtered out automatically if don't pass in preprocess_updated_prediction_files - might not have warning level set properly to detect f_pass < 1
[…]

### 2024-08-14 _targets.R
#82 delete code that excluded all constructed variables

@@ -242,40 +242,38 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                                                          all_prediction_data)),
      targets::tar_target(name = ManyEcoEvo_yi_results,
                          command =  ManyEcoEvo_yi %>% 
-                           dplyr::mutate(data = 
-                                           purrr::map(data, #TODO rm this filtering
-                                                      ~ dplyr::filter(.x, 
-                                                                      stringr::str_detect(response_variable_type, 
-                                                                                          "constructed", 
-                                                                                          negate = TRUE)))) %>% 
-                           prepare_response_variables(estimate_type = "yi",
-                                                      param_table = ManyEcoEvo:::analysis_data_param_tables, 
-                                                      dataset_standardise = "blue tit") %>%
-                           generate_yi_subsets() %>% #TODO: must be run after prepare_response_variables??
-                           apply_VZ_exclusions(3) %>%
-                           generate_exclusion_subsets() %>% #TODO: runs on ManyEcoEvo that contains Zr and yi results.
-                           compute_MA_inputs() %>%  #TODO lone join by "estimate_type" amongst join_by ("id_col") is suspicious!
-                           
-                           generate_outlier_subsets() %>% #TODO swapped order with previous line, but untested
-                           meta_analyse_datasets(filter_vars = NULL) #TODO requires col exclusion_set from generate_exclusion_subsets() but don't need that fun in this pipeline anymore
-     ),
-     targets::tar_target(name = ManyEcoEvo_yi_viz,
-                         command = make_viz(ManyEcoEvo_yi_results)),
-     targets::tar_target(name = ManyEcoEvo_study_summary,
-                         command = summarise_study(
-                           ManyEcoEvo, 
-                           ManyEcoEvo_results, 
-                           id_subsets = list(ManyEcoEvo:::effect_ids, 
-                                             ManyEcoEvo:::prediction_ids), 
-                           subset_names = c("effects", "predictions"), 
-                           filter_vars = rlang::exprs(exclusion_set == "complete",
-                                                      estimate_type == "Zr",
-                                                      publishable_subset == "All",
-                                                      expertise_subset == "All",
-                                                      collinearity_subset == "All")
-                         )),
-     tarchetypes::tar_quarto(name = README,
-                             path = "README.qmd"),
-     tarchetypes::tar_quarto(name = README_data_raw,
-                             path = here::here("data-raw/analysis_datasets/", "README.qmd"))
-)
[…]

### 2024-08-14 _targets.R
#97 linelength spacing / linting

@@ -175,7 +175,7 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                   drop_na(split_id) %>% #TODO, remove this `drop_na()` once we have fixed missing NA `gh issue view 109 -w`; `gh issue view 102 -w`
                   anti_join(., #TODO remove analyses where there are multiple submissions per split_id (~20) `gh issue view 109 -w`; `gh issue view 102 -w`
                             {count(., response_id, submission_id, analysis_id, split_id) %>% 
-                                filter(n>1)}) %>% 
+                                filter(n > 1)}) %>% 
                   group_by(response_id, submission_id, analysis_id, split_id) %>% 
                   tar_group(),
                 iteration = "group"),
@@ -243,14 +243,14 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
      targets::tar_target(name = ManyEcoEvo_yi_results,
                          command =  ManyEcoEvo_yi %>% 
                            dplyr::mutate(
-                             prepare_response_variables(estimate_type = "yi",
-                                                        param_table = ManyEcoEvo:::analysis_data_param_tables, 
-                                                        dataset_standardise = "blue tit") %>%
+                             prepare_response_variables(
+                               estimate_type = "yi",
+                               param_table = ManyEcoEvo:::analysis_data_param_tables, 
+                               dataset_standardise = "blue tit") %>%
                                generate_yi_subsets() %>% #TODO: must be run after prepare_response_variables??
                                apply_VZ_exclusions(3) %>%
                                generate_exclusion_subsets() %>% #TODO: runs on ManyEcoEvo that contains Zr and yi results.
                                compute_MA_inputs() %>%  #TODO lone join by "estimate_type" amongst join_by ("id_col") is suspicious!
-                               
                                generate_outlier_subsets() %>% #TODO swapped order with previous line, but untested
                                meta_analyse_datasets(filter_vars = NULL) #TODO requires col exclusion_set from generate_exclusion_subsets() but don't need that fun in this pipeline anymore
                            ),
@@ -274,6 +274,7 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                          tarchetypes::tar_quarto(name = README,
                                                  path = "README.qmd"),
                          tarchetypes::tar_quarto(name = README_data_raw,
-                                                 path = here::here("data-raw/analysis_datasets/", "README.qmd"))
+                                                 path = 
+                                                   here::here("data-raw/analysis_datasets/",
+                                                              "README.qmd"))
      )
-     

### 2024-08-14 _targets.R
#97 delete comment

@@ -27,8 +27,8 @@ pkgs <- c("tidyverse",
           "lme4",
           "multilevelmod",
           "metafor",
-          "parameters", # must be directly loaded else parameters::parameters() fails on lmerMod for some reason...
-          "ManyEcoEvo" #TODO rm from here and just call in tar_option_set(), but will need to rm all namespacing
+          "parameters",
+          "ManyEcoEvo" #TODO rm from here and just call in tar_option_set(), but will need to rm all namespacing, see gh issue #97
 ) 
 
 controller <- crew::crew_controller_local(

### 2024-08-14 _targets.R
#88 tar_make.R error - rm left over line from #82

@@ -242,7 +242,6 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                                                          all_prediction_data)),
      targets::tar_target(name = ManyEcoEvo_yi_results,
                          command =  ManyEcoEvo_yi %>% 
-                           dplyr::mutate(
                              prepare_response_variables(
                                estimate_type = "yi",
                                param_table = ManyEcoEvo:::analysis_data_param_tables, 
@@ -277,4 +276,3 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                                                  path = 
                                                    here::here("data-raw/analysis_datasets/",
                                                               "README.qmd"))
-     )

### 2024-08-14 _targets.R
#97 reindent after fixing prev commit
8b438cb9677a842ec89b1aafd4e6ec2d8601a7a5

@@ -189,7 +189,7 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                 error = "continue" #TODO, run without continue and check for problems
      ),
      tar_target(augmented_data,
-                command = if(!rlang::is_na(submission_data)){ 
+                command = if(!rlang::is_na(submission_data)) { 
                   augment_prediction_data(.data = submission_data, 
                                           checks = groups$checks, 
                                           dataset = groups$dataset)
@@ -200,7 +200,7 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                 error = "stop",
                 pattern = map(submission_data, groups)),
      tar_target(validated_augmented_data,
-                command = if(!rlang::is_na(augmented_data)){
+                command = if (!rlang::is_na(augmented_data)) {
                   validate_predictions(data_set = groups$dataset, 
                                        input = augmented_data %>% 
                                          ungroup(), 
@@ -213,7 +213,7 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                 pattern = map(augmented_data, groups)
      ),
      tar_target(prediction_checks,
-                command = if(!rlang::is_na(validated_augmented_data)){
+                command = if(!rlang::is_na(validated_augmented_data)) {
                   pointblank::interrogate(validated_augmented_data) %>% 
                     pointblank::get_agent_report(., display_table = FALSE)
                 }else{
@@ -242,37 +242,38 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                                                          all_prediction_data)),
      targets::tar_target(name = ManyEcoEvo_yi_results,
                          command =  ManyEcoEvo_yi %>% 
-                             prepare_response_variables(
-                               estimate_type = "yi",
-                               param_table = ManyEcoEvo:::analysis_data_param_tables, 
-                               dataset_standardise = "blue tit") %>%
-                               generate_yi_subsets() %>% #TODO: must be run after prepare_response_variables??
-                               apply_VZ_exclusions(3) %>%
-                               generate_exclusion_subsets() %>% #TODO: runs on ManyEcoEvo that contains Zr and yi results.
-                               compute_MA_inputs() %>%  #TODO lone join by "estimate_type" amongst join_by ("id_col") is suspicious!
-                               generate_outlier_subsets() %>% #TODO swapped order with previous line, but untested
[…]

### 2024-08-14 README.qmd
#97 update README explanation of targets script

@@
 -   Reproducing the analysis in *Gould et al.* using your own many-analyst style data
+
+[^1]: Gould, E., Fraser, H., Parker, T.
+*et al.* (2023).
+Same data, different analysts: Variation in effect sizes due to analytical decisions in ecology and evolutionary biology \[Preprint\].
+Ecology and Evolutionary Biology.
+https://doi.org/10.32942/X2GG62
 
@@
 2.  Run `renv::restore()` to load the packages used in the analysis pipeline locally on your machine (see [`renv::`](https://rstudio.github.io/renv/index.html) for details)
-3.  Run `tar_destroy()` to remove any record and caches of existing targets
+3.  Run `targets::tar_destroy()` to remove any record and caches of existing targets
 4.  Run `targets::tar_make()` in your console, depending on the power of your machine, the analysis pipeline will take between 2 and 7 minutes to execute (plus or minus some!)
@@
 ```
+
+The script that generates datasets used in the `ManyEcoEvo::` package is located in [`ManyEcoEvo/data-raw/tar_make.R`](https://github.com/egouldo/ManyEcoEvo/blob/main/data-raw/tar_make.R).
 
@@
 ```
-
-[^1]: Gould, E., Fraser, H., Parker, T.
-    *et al.* (2023).
-    Same data, different analysts: Variation in effect sizes due to analytical decisions in ecology and evolutionary biology \[Preprint\].
-    Ecology and Evolutionary Biology.
-    https://doi.org/10.32942/X2GG62

### 2024-08-29 R/generate_outlier_subsets.R
bug!: #130 correctly unquote filter_vars to shoosh warning
```r
#> Warning: Unquoting language objects with `!!!` is deprecated as of rlang 0.4.0. Please
#> use `!!` instead.
#>
#> # Bad: dplyr::select(data, !!!enquo(x))
#>
#> # Good: dplyr::select(data, !!enquo(x)) # Unquote single quosure
#> dplyr::select(data, !!!enquos(x)) # Splice list of quosures
```

@@ -221,7 +221,7 @@ apply_slice_conditionally <- function(x, filter_vars){
                                  exclusion_set } 
                              else {"complete"}), {
     x %>%
-      filter(!!!filter_vars) %>%
+      filter(!!filter_vars) %>%
       mutate(data = 
                pmap(list(data, outcome_colname, n_min, n_max),
                     .f = ~ slice_conditionally(..1, 

### 2024-08-29 R/meta_analyse_datasets.R
docs: fix typo

@@ -41,7 +41,7 @@
 #' - using `"Zr"` as the standardised effect size and `"VZr"` as the standard error when `estimate_type` is `"Zr"`.
 #' - using `"Z"` as the standardised out-of-sample estimate and `"VZ" `as the standardised out-of-sample estimate error when `estimate_type` is one of `c("yi", "y25", "y50", "y75")`.
 #' 
-#' The function will check if the `data` dataframe contains the required columns for meta-analysis, including any variable names specified in calls to the `filter_vars` argument. If the required functions do not exist then the function will stop with an error.
+#' The function will check if the `data` dataframe contains the required columns for meta-analysis, including any variable names specified in calls to the `filter_vars` argument. If the required columns do not exist then the function will stop with an error.
 #'  
 #' Function assumes that if argument `outcome_variable` is supplied, then `outcome_SE` is also supplied, and conversely, if `outcome_SE` is not supplied, then neither is `outcome_variable` (*TODO* not yet checked in function).
 #' 

### 2024-08-29 _targets.R
bug!: fix incorrect result of `filter_vars` for `yi` pipeline output build!: do not `generate_exclusion_subsets()` for `yi` pipeline - no effect. docs!: added explanation in vignette

@@ -269,7 +269,6 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                              VZ_colname = list("eucalyptus" = "se_log", 
                                                "blue tit" = "VZ"), 
                              VZ_cutoff = 3) %>%
-                           generate_exclusion_subsets() %>% #TODO: runs on ManyEcoEvo that contains Zr and yi results; DELETE, not needed
                            generate_outlier_subsets(
                              outcome_variable = 
                                list(dataset = 
@@ -286,7 +285,7 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                              outcome_SE = 
                                list(dataset = 
                                       list("eucalyptus" = "se_log", "blue tit" = "VZ")),
-                             filter_vars = rlang::exprs(exclusion_set == "complete")) #TODO requires col exclusion_set from generate_exclusion_subsets() but don't need that fun in this pipeline anymore
+                             filter_vars = NULL) 
      ),
      targets::tar_target(name = ManyEcoEvo_yi_viz,
                          command = make_viz(ManyEcoEvo_yi_results)),

### 2024-08-29 R/make_viz.R
bug!: generalise `make_viz()`
data subset columns now NOT explicitly named, only model outputs from `meta_analyse_datasets()` and `prepare_response_variables()`

---

fixes for #130 broke `make_viz()`

@@ -38,57 +38,35 @@ make_viz <- function(data) {
   if (any(str_detect(unique(data$estimate_type), pattern = "Zr"))) {
     data_Zr <- data %>%
       filter(estimate_type == "Zr") %>%
-      group_by(exclusion_set, dataset, estimate_type, publishable_subset, expertise_subset, collinearity_subset, data) %>%
-      pivot_longer(
-        names_to = "model_name",
-        values_to = "model",
-        cols = c(
-          -exclusion_set,
-          -dataset,
-          -estimate_type,
-          -data,
-          -diversity_data,
-          -diversity_indices,
-          -effects_analysis,
-          -publishable_subset,
-          -expertise_subset,
-          -collinearity_subset
-        )
-      ) %>%
-      ungroup() %>%
       select(
         -data,
         -diversity_data,
         -diversity_indices,
         -effects_analysis
+      ) %>% 
+      pivot_longer(names_to = "model_name", values_to = "model",
+                   cols = c(starts_with("MA_mod"), 
+                            "sorensen_glm", 
+                            starts_with("box_cox_rating"), 
+                            "uni_mixed_effects")
       )
   }
   
   if (any(str_detect(unique(data$estimate_type), "y"))) {
     data_yi <- data %>%
       filter(estimate_type %in% c("yi", "y25", "y50", "y75")) %>%
-      group_by(exclusion_set, dataset, estimate_type, data) %>%
-      pivot_longer(
-        names_to = "model_name",
-        values_to = "model",
-        cols = c(
-          -exclusion_set,
-          -dataset,
-          -estimate_type,
-          -data,
-          -diversity_data,
-          -diversity_indices,
-          -effects_analysis
-        )
-      ) %>%
-      ungroup() %>%
       select(
         -data,
         -diversity_data,
         -diversity_indices,
         -effects_analysis
-      ) %>%
-      mutate(publishable_subset = NA)
+      ) %>% 
+      pivot_longer(names_to = "model_name", values_to = "model",
+                   cols = c(starts_with("MA_mod"), 
+                            "sorensen_glm", 
+                            starts_with("box_cox_rating"), 
+                            "uni_mixed_effects")
+      )
   }
   
   if (exists("data_Zr") & exists("data_yi")) {

### 2024-08-29 _targets.R
build!: do not run outlier exclusion on `yi` results #130
was originally only included to generate hard-coded columns, now no longer needed with #121 / #130 updates, and was never planned: <https://egouldo.github.io/ManyAnalysts/#out-of-sample-predictions-y_i-2>

@@ -275,14 +275,6 @@ list(tarchetypes::tar_file_read(name = euc_reviews,
                              VZ_colname = list("eucalyptus" = "se_log", 
                                                "blue tit" = "VZ"), 
                              VZ_cutoff = 3) %>%
-                           generate_outlier_subsets(
-                             outcome_variable = 
-                               list(dataset = 
-                                      list("eucalyptus" = "mean_log", 
-                                           "blue tit" = "Z")), 
-                             n_min = -3, 
-                             n_max = -3, 
-                             ignore_subsets = NULL) %>%
                            compute_MA_inputs() %>%  
                            meta_analyse_datasets(
                              outcome_variable = 

### 2024-08-29 R/make_viz.R
bug!: revert back to using `broom.mixed::tidy()` #130
`broom::tidy()` doesn't have method for `lmerMod` class

@@ -9,7 +9,7 @@
 #' @import dplyr
 #' @importFrom purrr map_if map2 pmap possibly
 #' @importFrom stringr str_detect
-#' @importFrom broom tidy
+#' @importFrom broom.mixed tidy
 #' @importFrom performance performance
 #' @importFrom metaviz viz_funnel
 #' @importFrom ggplot2 ggplot
@@ -23,7 +23,7 @@ make_viz <- function(data) {
   # ---- Define Helper Functions ----
   
   tidy_mod <- function(mod) {
-    broom::tidy(mod, 
+    broom.mixed::tidy(mod, 
                 conf.int = TRUE,
                 include_studies = TRUE)
   }

### 2024-09-09 R/augment_prediction_data.R
- docs!: #102 add roxygen imports to function doc

@@ -6,7 +6,7 @@
 #' Where there are missing variables in `.data` or `checks` is missing,
 #' `NA` will be returned for the augmented prediction data instead.
 #' @param .data A data.frame of out of-sample-predictions analyst submission data
-#' @param checks A data.frame of [pointblank::] interrogation output for `.data`
+#' @param checks A data.frame of `pointblank::` interrogation output for `.data`
 #' @param dataset A character string equal to either "blue tit" or "eucalyptus"
 #'
 #' @return A dataframe of individual analyst submission containing augmented
@@ -16,6 +16,15 @@
 #' @examples
 #' # for testing and dev purposes:
 #' # safe_augment <- purrr:::safely(augment_prediction_data)
+#' @import dplyr
+#' @importFrom cli cli_abort cli_alert
+#' @importFrom purrr flatten_df flatten_chr
+#' @importFrom stringr str_detect
+#' @importFrom purrr set_names
+#' @importFrom tibble tibble
+#' @importFrom readr parse_number locale
+#' @importFrom tidyr drop_na
+#' @importFrom rlang is_na
 augment_prediction_data <- function(.data, checks, dataset) {
   if (is.logical(.data)) {
     return(NA)

### 2024-09-09 R/convert_predictions.R

@@ -10,6 +10,9 @@
 #' @importFrom cli cli_alert_warning cli_abort
 #' @importFrom data.table setnames
 #' @importFrom pointblank has_columns
+#' @importFrom tibble tibble deframe
+#' @importFrom purrr discard
+#' @importFrom tidyselect any_of
 #' @family Back-transformation
 #' @seealso [rename_prediction_cols()]
 convert_predictions <- function(augmented_data,

### 2024-09-09 R/convert_predictions.R
- refactor!: change method for renaming prediction columns (generalise beyond BT / Euc)
And remove function`rename_prediction_cols()` since it is now redundant

@@ -42,19 +42,19 @@ convert_predictions <- function(augmented_data,
       USE.NAMES = TRUE,
       SIMPLIFY = "matrix"
     )
-
+    
     vconvert_double_transformation <- Vectorize(
       FUN = conversion_2,
       vectorize.args = c("beta", "se"),
       USE.NAMES = TRUE,
       SIMPLIFY = TRUE
     )
-
+    
     # Define input variables to conversion fns
-
+    
     key_var <- augmented_data %>%
       dplyr::select(dplyr::contains(c("scenario", "SurveyID")))
-
+    
     beta_vals <- if (names(key_var) == "scenario") {
       # Extracting yi estimates to supply to beta arg in vconvert
       if (!pointblank::has_columns(augmented_data, "estimate")) {
@@ -67,9 +67,9 @@ convert_predictions <- function(augmented_data,
       }
       augmented_data$fit
     }
-
+    
     # Apply Conversion w Helper Funs & Input Variables
-
+    
     converted <- if (transformation_type %nin% "double_transformation") {
       vconvert(
         beta = beta_vals,
@@ -79,12 +79,12 @@ convert_predictions <- function(augmented_data,
       ) %>%
         t()
     } else { # Back-transform response AND link-function
-
+      
       if (any(rlang::is_na(response_transformation), rlang::is_na(link_fun))) {
         cli::cli_alert_warning("Missing Value for {.arg response_transformation}, returning {.val NA}")
         out <- rlang::na_cpl
       }
-
+      
       vconvert_double_transformation(
         beta = beta_vals,
         se = augmented_data$se.fit,
@@ -94,47 +94,29 @@ convert_predictions <- function(augmented_data,
       ) %>%
         t()
     }
-
+    
+    names_lookup <- tibble(input_names = augmented_data %>% 
+                             colnames() %>% 
+                             discard(~ .x == colnames(key_var))) %>% 
+      mutate(new_names = 
+               case_match(input_names, 
+                          "fit" ~ "mean_origin", 
+                          "estimate" ~ "mean_origin", 
+                          "se.fit" ~ "se_origin", 
+                          "ci.low" ~ "lower", 
+                          "ci.hi" ~ "upper", 
+                          .default = NA)) %>%  
+      rows_append(tibble(input_names = "sd.fit",
+                         new_names = "sd_origin")) %>% 
+      deframe()
+    
     # reshape conversion outputs
-
     out <- converted %>%
       dplyr::as_tibble() %>%
[…]

### 2024-09-09 R/prepare_response_variables.R
- refactor!: rm unnecessary arguments to `back_transform_response_vars_yi()`, update call of function within `prepare_response_variables_yi()` #97
And update associated roxygen code, especially imports #102

@@ -116,14 +116,9 @@ prepare_response_variables <- function(data,
     out <- out %>%
       ungroup() %>%
       dplyr::mutate(
-        data = purrr::map2( #TODO assign to data or not?
+        data = purrr::map(
           .x = data, 
-          .y = dataset,
-          .f = ~ back_transform_response_vars_yi(
-            dat = .x,
-            estimate_type = !!{estimate_type},
-            dataset = .y
-          )
+          .f = ~ back_transform_response_vars_yi(.x)
         ),
         diversity_data = 
           map2(

### 2024-09-09 R/prepare_response_variables_yi.R

@@ -9,30 +9,22 @@
 #' `estimate_type` is used to specify the type of estimate to be standardised and parsed to [back_transform_response_vars_yi()]
 #' @seealso [back_transform_response_vars_yi()]. To be called prior to [generate_yi_subsets()].
 #' @import dplyr
-#' @importFrom purrr map2
+#' @importFrom purrr map2 map
+#' @importFrom pointblank expect_col_exists
 #' @family targets-pipeline functions
 #' @family Multi-dataset Wrapper Functions
 #' @export
-prepare_response_variables_yi <- function(data,
-                                          estimate_type = character(1L),
-                                          param_table = NULL) {
+prepare_response_variables_yi <- function(data) {
   stopifnot(is.data.frame(data))
-  # TODO run checks on data
-  match.arg(estimate_type, choices = c("yi", "y25", "y50", "y75"), several.ok = FALSE)
+  
+  pointblank::expect_col_exists(data, c("data", "diversity_data"))
   
   out <- data %>%
     ungroup() %>%
     dplyr::mutate(
-      data = purrr::map2(
-        .x = data, .y = dataset,
-        .f = ~ back_transform_response_vars_yi(
-          dat = .x,
-          estimate_type = !!{
-            estimate_type
-          },
-          param_table,
-          dataset = .y
-        )
+      data = purrr::map(
+        .x = data, 
+        .f = prepare_response_variables_yi
       ),
       diversity_data = purrr::map2(
         .x = diversity_data,
@@ -47,10 +39,10 @@ prepare_response_variables_yi <- function(data,
 #' Back-transform analyst `yi` estiamtes to the response scale
 #'
 #' @param data dataframe of out of sample predictions analyst submission data
-#' @param estimate_type The type of estimate to be standardised. Character vector of length 1, whose value may be  "yi", "y25", "y50", "y75".
-#' @param dataset One of either "blue tit" or "eucalyptus"
-#'
 #' @return A tibble of analyst data with standardised values contained in a list-column called 'back_transformed_data'
+#' @details
+#' `data` must contain the columns: `id_col`, `augmented_data`, `transformation`, `response_transformation_status`, where `augmented_data` is a list-column of dataframes containing the analyst predictions, `transformation` is the transformation used in the model, and `response_transformation_status` is the status of the response transformation.
+#' 
 #' @export
 #' @import dplyr
 #' @importFrom purrr pmap
@@ -58,12 +50,9 @@ prepare_response_variables_yi <- function(data,
[…]

### 2024-09-09 R/back_transformations.R
- bug, refactor!: extract SD in addition to SE for analysis #151

@@ -25,15 +25,22 @@ log_back <- function(beta, se, sim) {
   original <- exp(simulated) %>% # exponential = inverse of log
     na.omit()
   m_est <- mean(original)
-  se_est <- sd(original) / sqrt(length(original))
+  sd_est <- sd(original)
+  se_est <- sd_est / sqrt(length(original))
   quantiles <- quantile(original, c(0.025, 0.975), na.rm = TRUE)
-  set <- data.frame(mean_origin = m_est, se_origin = se_est, lower = quantiles[[1]], upper = quantiles[[2]])
+  set <- data.frame(mean_origin = m_est, 
+                    se_origin = se_est,
+                    sd_origin = sd_est,
+                    lower = quantiles[[1]], 
+                    upper = quantiles[[2]])
+  
   if (flatten_dbl(set) %>%
     map_lgl(.f = ~ is.na(.x) | is.nan(.x) | is.infinite(.x)) %>%
     any()) {
     cli::cli_alert_danger("{.val NA}, {.val Inf} or {.val NaN} returned during back-transformation of effect sizes and standard errors.")
   }
   cli::cli_alert_success("Applied back-transformation for log-transformed effect sizes or out-of-sample predictions, using {.val {sim}} simulations.")
+  
   return(set)
 }
 
@@ -45,9 +52,14 @@ logit_back <- function(beta, se, sim) {
   original <- plogis(simulated) %>% # invlogit
     na.omit()
   m_est <- mean(original)
-  se_est <- sd(original) / sqrt(length(original))
+  sd_est <- sd(original)
+  se_est <- sd_est / sqrt(length(original))
   quantiles <- quantile(original, c(0.025, 0.975), na.rm = TRUE)
-  set <- data.frame(mean_origin = m_est, se_origin = se_est, lower = quantiles[[1]], upper = quantiles[[2]])
+  set <- data.frame(mean_origin = m_est, 
+                    se_origin = se_est, 
+                    sd_origin = sd_est,
+                    lower = quantiles[[1]], 
+                    upper = quantiles[[2]])
   if (flatten_dbl(set) %>%
     map_lgl(.f = ~ is.na(.x) | is.nan(.x) | is.infinite(.x)) %>%
     any()) {
@@ -65,9 +77,15 @@ probit_back <- function(beta, se, sim) {
   original <- pnorm(simulated) %>% # inv-probit
     na.omit()
[…]

### 2024-09-09 R/conversion.R

@@ -73,7 +73,7 @@ conversion <- function(beta, se, transformation, sim = 10000) {
       pluck(1, 2) %>%
       as.numeric()
     if (rlang::is_na(n)) {
-      return(data.frame(mean_origin = NA, m_est = NA, se_origin = NA, lower = NA, upper = NA))
+      return(data.frame(mean_origin = NA, m_est = NA, se_origin = NA, sd_origin = NA, lower = NA, upper = NA))
     } else {
       power_back(beta, se, sim, n)
     }
@@ -82,12 +82,12 @@ conversion <- function(beta, se, transformation, sim = 10000) {
       pluck(1, 3) %>%
       as.numeric()
     if (rlang::is_na(n)) {
-      return(data.frame(mean_origin = NA, m_est = NA, se_origin = NA, lower = NA, upper = NA))
+      return(data.frame(mean_origin = NA, m_est = NA, se_origin = NA, sd_origin = NA, lower = NA, upper = NA))
     } else {
       divide_back(beta, se, sim, n)
     }
   } else if (transformation == "double_transformation") {
-    return(data.frame(mean_origin = NA, m_est = NA, se_origin = NA, lower = NA, upper = NA))
+    return(data.frame(mean_origin = NA, m_est = NA, se_origin = NA, sd_origin = NA, lower = NA, upper = NA))
   } else {
     identity_back(beta, se, sim) # TODO change conditional logic to ensure strange transformations not put through here
   }

### 2024-09-09 R/log_transform.R

@@ -19,11 +19,13 @@ log_transform <- function(estimate = numeric(1L),
     na.omit()
   
   m_est <- mean(log_simulated)
-  std.error_est <- sd(log_simulated) / sqrt(length(log_simulated))
+  sd_est <- sd(log_simulated)
+  std.error_est <- sd_est / sqrt(length(log_simulated))
   quantiles <- quantile(log_simulated, c(0.025, 0.975), na.rm = TRUE)
   
   out <- data.frame(mean_log = m_est, 
                     se_log = std.error_est, 
+                    sd_log = sd_est,
                     lower = quantiles[[1]], 
                     upper = quantiles[[2]])
   

### 2024-09-09 manuscript/manuscript/investigate_back.R
- analysis: #151 investigate extreme precision after changing back-transformation fns

@@ -1,0 +1,188 @@
+out <- targets::tar_read(ManyEcoEvo_yi) %>% 
+  mutate(
+    data = 
+      map_if(data, 
+             ~ filter(.x, 
+                      stringr::str_detect(
+                        response_variable_name, 
+                        "average.proportion.of.plots.containing",
+                        negate = TRUE)),
+             .p = dataset == "eucalyptus")) %>%   
+  mutate(
+    diversity_data =
+      map2(
+        .x = diversity_data,
+        .y = data,
+        .f = ~ semi_join(.x, .y, join_by(id_col)) %>% 
+          distinct()
+      )
+  ) %>% filter(dataset == "eucalyptus") %>% 
+  pluck("data", 1)
+
+back_transformed_se <- 
+  back_transform_response_vars_yi(out) %>% 
+  select("id_col", 
+         ends_with("data"), 
+         starts_with("transformation"), 
+         -review_data) %>% 
+  rowwise(id_col) %>% 
+  mutate(yi_data = list(left_join(augmented_data, back_transformed_data, 
+                                  by = join_by(SurveyID), 
+                                  suffix = c(".aug", ".back")))) %>% 
+  unnest(yi_data) %>% 
+  ungroup %>% 
+  select(contains("id"), starts_with("fit"), starts_with("se"), starts_with("sd"), transformation_type) %>% 
+  rename("sd.fit.back" = "sd.fit") 
+
+check_transformations_se <- 
+  back_transformed_se %>% 
+  rowwise(id_col, SurveyID) %>% 
+  mutate(log_transformed_se = list(log_transform(estimate = fit.back, 
+                                                 std.error = se.fit.back, 
+                                                 sim = 100) %>% 
+                                     rename_with(~ paste0(.x, "SE"))),
+         log_transformed_sd = list(log_transform(estimate = 
+                                                   fit.back, 
+                                                 std.error = sd.fit.back, 
+                                                 sim = 100) %>% 
+                                     rename_with(~ paste0(.x, "SD")))
+  ) %>% 
+  unnest(cols = c(log_transformed_se, log_transformed_sd)) %>% 
+  relocate(contains("mean_log"), .after = starts_with("fit")) %>% 
+  relocate(contains("se_log"), .after = starts_with("se.")) %>% 
+  relocate(contains("sd_log"), .after = starts_with("sd.")) %>% 
[…]

### 2024-09-09 manuscript/manuscript/investigate_back.R
#151 update file for reprex generation, output objects and load pkg with devtools

@@ -1,3 +1,4 @@
+devtools::load_all()
 out <- targets::tar_read(ManyEcoEvo_yi) %>% 
   mutate(
     data = 
@@ -146,6 +147,13 @@ back_transformed_sd_sims <-
   relocate(contains("sd_log"), .after = starts_with("sd.")) %>% 
   select(-contains("ci"), -contains("lower"), -contains("upper")) 
 
+check_transformations_se
+
+back_transformed_se_sims
+
+check_transformations_sd
+
+back_transformed_sd_sims
 
 # ---- blue tit ---
     
@@ -186,3 +194,5 @@ check_transformations_se <-
   relocate(contains("se_log"), .after = starts_with("se.")) %>% 
   relocate(contains("sd_log"), .after = starts_with("sd.")) %>% 
   select(-contains("ci"), -contains("lower"), -contains("upper")) 
+
+check_transformations_se

### 2024-09-09 manuscript/manuscript/investigate_back.R
- analysis #151 add reprex chunk options to quiet messages, add headings

@@ -1,4 +1,6 @@
 devtools::load_all()
+
+#+ message = FALSE, warning = FALSE
 out <- targets::tar_read(ManyEcoEvo_yi) %>% 
   mutate(
     data = 
@@ -147,17 +149,22 @@ back_transformed_sd_sims <-
   relocate(contains("sd_log"), .after = starts_with("sd.")) %>% 
   select(-contains("ci"), -contains("lower"), -contains("upper")) 
 
-check_transformations_se
+#' # Euc checking
 
-back_transformed_se_sims
+#+ 
+# ---- report euc results ----
+check_transformations_se %>% knitr::kable()
 
-check_transformations_sd
+back_transformed_se_sims %>%  knitr::kable()
 
-back_transformed_sd_sims
+check_transformations_sd %>%  knitr::kable()
 
+back_transformed_sd_sims %>% knitr::kable()
+
+#' # BT checking
+
+#+ message = FALSE, warning = FALSE
 # ---- blue tit ---
-    
-    
 bt <- targets::tar_read(ManyEcoEvo_yi) %>% filter(dataset == "blue tit") %>% 
   pluck("data", 1)
 
@@ -195,4 +202,5 @@ check_transformations_se <-
   relocate(contains("sd_log"), .after = starts_with("sd.")) %>% 
   select(-contains("ci"), -contains("lower"), -contains("upper")) 
 
-check_transformations_se
+#+ 
+check_transformations_se %>% knitr::kable()

### 2024-09-09 manuscript/manuscript/investigate_back.R
- analysis #151 add additional reprex chunk to quiet output

@@ -183,6 +183,7 @@ back_transformed_se_bt <-
   select(contains("id"), starts_with("estimate"), starts_with("se"), starts_with("sd"), transformation_type) %>% 
   rename("sd.fit.back" = "sd.fit") 
 
+#+ message = FALSE, warning = FALSE
 check_transformations_se <- 
   back_transformed_se %>% 
   rowwise(id_col, scenario) %>% 

### 2024-09-09 cilia-stag_reprex.R
#151 add analysis reprex

@@ -1,0 +1,213 @@
+#' ---
+#' output:
+#'   reprex::reprex_document:
+#'     style: TRUE
+#' ---
+
+devtools::load_all()
+
+#+ message = FALSE, warning = FALSE
+out <- targets::tar_read(ManyEcoEvo_yi) %>% 
+  mutate(
+    data = 
+      map_if(data, 
+             ~ filter(.x, 
+                      stringr::str_detect(
+                        response_variable_name, 
+                        "average.proportion.of.plots.containing",
+                        negate = TRUE)),
+             .p = dataset == "eucalyptus")) %>%   
+  mutate(
+    diversity_data =
+      map2(
+        .x = diversity_data,
+        .y = data,
+        .f = ~ semi_join(.x, .y, join_by(id_col)) %>% 
+          distinct()
+      )
+  ) %>% filter(dataset == "eucalyptus") %>% 
+  pluck("data", 1)
+
+back_transformed_se <- 
+  back_transform_response_vars_yi(out) %>% 
+  select("id_col", 
+         ends_with("data"), 
+         starts_with("transformation"), 
+         -review_data) %>% 
+  rowwise(id_col) %>% 
+  mutate(yi_data = list(left_join(augmented_data, back_transformed_data, 
+                                  by = join_by(SurveyID), 
+                                  suffix = c(".aug", ".back")))) %>% 
+  unnest(yi_data) %>% 
+  ungroup %>% 
+  select(contains("id"), starts_with("fit"), starts_with("se"), starts_with("sd"), transformation_type) %>% 
+  rename("sd.fit.back" = "sd.fit") 
+
+check_transformations_se <- 
+  back_transformed_se %>% 
+  rowwise(id_col, SurveyID) %>% 
+  mutate(log_transformed_se = list(log_transform(estimate = fit.back, 
+                                                 std.error = se.fit.back, 
+                                                 sim = 100) %>% 
+                                     rename_with(~ paste0(.x, "SE"))),
+         log_transformed_sd = list(log_transform(estimate = 
+                                                   fit.back, 
+                                                 std.error = sd.fit.back, 
+                                                 sim = 100) %>% 
+                                     rename_with(~ paste0(.x, "SD")))
+  ) %>% 
+  unnest(cols = c(log_transformed_se, log_transformed_sd)) %>% 
+  relocate(contains("mean_log"), .after = starts_with("fit")) %>% 
[…]

### 2024-09-09 R/back_transformations.R
- fix!: #151 revert to taking sd() from normalised distribution prior to back-transformation and assigning as SE
And update wrapper functions so that NA's return dataframes matched to dim and str from _back functions

@@ -25,12 +25,10 @@ log_back <- function(beta, se, sim) {
   original <- exp(simulated) %>% # exponential = inverse of log
     na.omit()
   m_est <- mean(original)
-  sd_est <- sd(original)
-  se_est <- sd_est / sqrt(length(original))
+  se_est <- sd(original)
   quantiles <- quantile(original, c(0.025, 0.975), na.rm = TRUE)
   set <- data.frame(mean_origin = m_est, 
                     se_origin = se_est,
-                    sd_origin = sd_est,
                     lower = quantiles[[1]], 
                     upper = quantiles[[2]])
   
@@ -52,12 +50,10 @@ logit_back <- function(beta, se, sim) {
   original <- plogis(simulated) %>% # invlogit
     na.omit()
   m_est <- mean(original)
-  sd_est <- sd(original)
-  se_est <- sd_est / sqrt(length(original))
+  se_est <- sd(original)
   quantiles <- quantile(original, c(0.025, 0.975), na.rm = TRUE)
   set <- data.frame(mean_origin = m_est, 
                     se_origin = se_est, 
-                    sd_origin = sd_est,
                     lower = quantiles[[1]], 
                     upper = quantiles[[2]])
   if (flatten_dbl(set) %>%
@@ -77,12 +73,10 @@ probit_back <- function(beta, se, sim) {
   original <- pnorm(simulated) %>% # inv-probit
     na.omit()
   m_est <- mean(original)
-  sd_est <- sd(original)
-  se_est <- sd_est / sqrt(length(original))
+  se_est <- sd(original)
   quantiles <- quantile(original, c(0.025, 0.975), na.rm = TRUE)
   set <- data.frame(mean_origin = m_est, 
                     se_origin = se_est, 
-                    sd_origin = sd_est,
                     lower = quantiles[[1]], 
                     upper = quantiles[[2]])
   
@@ -103,12 +97,10 @@ inverse_back <- function(beta, se, sim) {
   original <- 1 / simulated %>% # inverse
     na.omit()
   m_est <- mean(original)
-  sd_est <- sd(original)
-  se_est <- sd_est / sqrt(length(original))
+  se_est <- sd(original)
   quantiles <- quantile(original, c(0.025, 0.975), na.rm = TRUE)
   set <- data.frame(mean_origin = m_est, 
                     se_origin = se_est, 
-                    sd_origin = sd_est,
[…]

### 2024-09-09 R/conversion.R

@@ -67,13 +67,16 @@ conversion <- function(beta, se, transformation, sim = 10000) {
     square_root_back(beta, se, sim)
   } else if (transformation == "(power3)/100") {
     x100 <- divide_back(beta, se, sim, 100)
-    cube_back(x100$mean_origin, x100$se_origin, sim = 1000)
+    cube_back(x100$mean_origin, x100$se_origin, sim)
   } else if (stringr::str_detect(transformation, "power")) {
     n <- str_split(transformation, "power") %>%
       pluck(1, 2) %>%
       as.numeric()
     if (rlang::is_na(n)) {
-      return(data.frame(mean_origin = NA, m_est = NA, se_origin = NA, sd_origin = NA, lower = NA, upper = NA))
+      return(data.frame(mean_origin = NA, 
+                        se_origin = NA, 
+                        lower = NA, 
+                        upper = NA))
     } else {
       power_back(beta, se, sim, n)
     }
@@ -82,12 +85,18 @@ conversion <- function(beta, se, transformation, sim = 10000) {
       pluck(1, 3) %>%
       as.numeric()
     if (rlang::is_na(n)) {
-      return(data.frame(mean_origin = NA, m_est = NA, se_origin = NA, sd_origin = NA, lower = NA, upper = NA))
+      return(data.frame(mean_origin = NA, 
+                        se_origin = NA, 
+                        lower = NA, 
+                        upper = NA))
     } else {
       divide_back(beta, se, sim, n)
     }
   } else if (transformation == "double_transformation") {
-    return(data.frame(mean_origin = NA, m_est = NA, se_origin = NA, sd_origin = NA, lower = NA, upper = NA))
+    return(data.frame(mean_origin = NA, 
+                      se_origin = NA, 
+                      lower = NA, 
+                      upper = NA))
   } else {
     identity_back(beta, se, sim) # TODO change conditional logic to ensure strange transformations not put through here
   }

### 2024-09-09 R/log_transform.R

@@ -19,13 +19,11 @@ log_transform <- function(estimate = numeric(1L),
     na.omit()
   
   m_est <- mean(log_simulated)
-  sd_est <- sd(log_simulated)
-  std.error_est <- sd_est / sqrt(length(log_simulated))
+  se_est <- sd(log_simulated)
   quantiles <- quantile(log_simulated, c(0.025, 0.975), na.rm = TRUE)
   
   out <- data.frame(mean_log = m_est, 
-                    se_log = std.error_est, 
-                    sd_log = sd_est,
+                    se_log = se_est, 
                     lower = quantiles[[1]], 
                     upper = quantiles[[2]])
   

### 2024-09-09 cilia-stag_reprex.R
- #151 rm reprex and investigation script
noted in issue comments previously: https://github.com/egouldo/ManyEcoEvo/issues/151#issuecomment-2337011873

@@ -1,213 +1,0 @@
-#' ---
-#' output:
-#'   reprex::reprex_document:
-#'     style: TRUE
-#' ---
-
-devtools::load_all()
-
-#+ message = FALSE, warning = FALSE
-out <- targets::tar_read(ManyEcoEvo_yi) %>% 
-  mutate(
-    data = 
-      map_if(data, 
-             ~ filter(.x, 
-                      stringr::str_detect(
-                        response_variable_name, 
-                        "average.proportion.of.plots.containing",
-                        negate = TRUE)),
-             .p = dataset == "eucalyptus")) %>%   
-  mutate(
-    diversity_data =
-      map2(
-        .x = diversity_data,
-        .y = data,
-        .f = ~ semi_join(.x, .y, join_by(id_col)) %>% 
-          distinct()
-      )
-  ) %>% filter(dataset == "eucalyptus") %>% 
-  pluck("data", 1)
-
-back_transformed_se <- 
-  back_transform_response_vars_yi(out) %>% 
-  select("id_col", 
-         ends_with("data"), 
-         starts_with("transformation"), 
-         -review_data) %>% 
-  rowwise(id_col) %>% 
-  mutate(yi_data = list(left_join(augmented_data, back_transformed_data, 
-                                  by = join_by(SurveyID), 
-                                  suffix = c(".aug", ".back")))) %>% 
-  unnest(yi_data) %>% 
-  ungroup %>% 
-  select(contains("id"), starts_with("fit"), starts_with("se"), starts_with("sd"), transformation_type) %>% 
-  rename("sd.fit.back" = "sd.fit") 
-
-check_transformations_se <- 
-  back_transformed_se %>% 
-  rowwise(id_col, SurveyID) %>% 
-  mutate(log_transformed_se = list(log_transform(estimate = fit.back, 
-                                                 std.error = se.fit.back, 
-                                                 sim = 100) %>% 
-                                     rename_with(~ paste0(.x, "SE"))),
-         log_transformed_sd = list(log_transform(estimate = 
-                                                   fit.back, 
-                                                 std.error = sd.fit.back, 
-                                                 sim = 100) %>% 
-                                     rename_with(~ paste0(.x, "SD")))
-  ) %>% 
-  unnest(cols = c(log_transformed_se, log_transformed_sd)) %>% 
-  relocate(contains("mean_log"), .after = starts_with("fit")) %>% 
[…]

### 2024-09-09 manuscript/manuscript/investigate_back.R

@@ -1,207 +1,0 @@
-devtools::load_all()
-
-#+ message = FALSE, warning = FALSE
-out <- targets::tar_read(ManyEcoEvo_yi) %>% 
-  mutate(
-    data = 
-      map_if(data, 
-             ~ filter(.x, 
-                      stringr::str_detect(
-                        response_variable_name, 
-                        "average.proportion.of.plots.containing",
-                        negate = TRUE)),
-             .p = dataset == "eucalyptus")) %>%   
-  mutate(
-    diversity_data =
-      map2(
-        .x = diversity_data,
-        .y = data,
-        .f = ~ semi_join(.x, .y, join_by(id_col)) %>% 
-          distinct()
-      )
-  ) %>% filter(dataset == "eucalyptus") %>% 
-  pluck("data", 1)
-
-back_transformed_se <- 
-  back_transform_response_vars_yi(out) %>% 
-  select("id_col", 
-         ends_with("data"), 
-         starts_with("transformation"), 
-         -review_data) %>% 
-  rowwise(id_col) %>% 
-  mutate(yi_data = list(left_join(augmented_data, back_transformed_data, 
-                                  by = join_by(SurveyID), 
-                                  suffix = c(".aug", ".back")))) %>% 
-  unnest(yi_data) %>% 
-  ungroup %>% 
-  select(contains("id"), starts_with("fit"), starts_with("se"), starts_with("sd"), transformation_type) %>% 
-  rename("sd.fit.back" = "sd.fit") 
-
-check_transformations_se <- 
-  back_transformed_se %>% 
-  rowwise(id_col, SurveyID) %>% 
-  mutate(log_transformed_se = list(log_transform(estimate = fit.back, 
-                                                 std.error = se.fit.back, 
-                                                 sim = 100) %>% 
-                                     rename_with(~ paste0(.x, "SE"))),
-         log_transformed_sd = list(log_transform(estimate = 
-                                                   fit.back, 
-                                                 std.error = sd.fit.back, 
-                                                 sim = 100) %>% 
-                                     rename_with(~ paste0(.x, "SD")))
-  ) %>% 
-  unnest(cols = c(log_transformed_se, log_transformed_sd)) %>% 
-  relocate(contains("mean_log"), .after = starts_with("fit")) %>% 
-  relocate(contains("se_log"), .after = starts_with("se.")) %>% 
-  relocate(contains("sd_log"), .after = starts_with("sd.")) %>% 
-  select(-contains("ci"), -contains("lower"), -contains("upper")) 
-
[…]

### 2025-10-15 R/apply_sorensen_calc.R
Capitalise Sorensen

@@ -1,7 +1,6 @@
-#' Applies the sorensen diversity index calculation to variable diversity dataset
+#' Applies the Sorensen diversity index calculation to variable diversity dataset
 #'
 #' @param data A variable diversity dataset with columns for each unique variable used in all analyses. Values are `NA` if the analysis did not use that variable, and take the value of the variable as a character string if the analysis did use that variable. Each unique analysis is a row.
-#' 
 #' @seealso [calculate_sorensen_diversity_index()]
 #'
 #' @return A tibble containing the variables `id_col`, `mean_diversity_index` and `num_variables`

### 2025-10-15 R/calculate_descriptive_statistics.R
code formatting, make long for ease of reading

@@ -191,7 +191,9 @@ prepare_diversity_summary_data <- function(data, data_subset_name = "all", id_su
       map(id_subsets, left_join, ., by = join_by("id_col"))
     }) %>%
     list_flatten() %>%
-    tibble(data = ., subset_name = c(data_subset_name, subset_names))
+    tibble(data = ., subset_name = 
+             c(data_subset_name, 
+               subset_names))
 }
 
 #' Prepare data for summarising analyst summary statistics
@@ -477,13 +479,20 @@ summarise_study <- function(ManyEcoEvo, ManyEcoEvo_results, id_subsets, subset_n
   
   # ----- Combine Outputs -----
   
-  list(subsets_tibble, subsets_tibble_variables, subsets_tibble_sorensen) %>%
+  list(subsets_tibble, 
+       subsets_tibble_variables, 
+       subsets_tibble_sorensen) %>%
     reduce(left_join, by = join_by("data", "subset_name")) %>%
     left_join(Total_Teams_Per_Analysis,
               by = join_by("subset_name" == "subset")
     ) %>%
     reduce2(
-      .x = list(SorensenSummary, teams_per_subset, Table4, Table3, Table2, Table1),
+      .x = list(SorensenSummary, 
+                teams_per_subset, 
+                Table4, 
+                Table3, 
+                Table2, 
+                Table1),
       .y = c(
         "sorensen_summary",
         "teams_per_subset",

### 2025-10-15 data-raw/create_internal_pkg_data.R
Update comment with author source for future

@@ -364,7 +364,7 @@ prediction_ids <- tibble::tribble(
   "Childers-1-1-1",
   "Childers-2-2-1",
   "Cessnock-1-1-1"
-) # TODO ask HF where/how derived (used data pasta to copy from HF's files)
+) # Derived by HF
 
 # ------ Create transformation_tbl -----
 

### 2025-10-15 data-raw/create_internal_pkg_data.R
Rm comments + fix indentation

@@ -380,18 +380,18 @@ transformation_tbl <- tribble(
   "scaling and centering", "identity",
   "mean centered and standardized", "identity",
   "log", "log",
-  "orderNorm", NA, # TODO, ensure that this is the best behaviour - we need to exclude this first, rather than let it through here.. because else it gets passed through identity_back() inside conversion()
+  "orderNorm", NA,
   "divided.by.14", "divided.by.14",
   "square.root", "square_root",
   "back.transformed", "back.transformed",
   "z.score", "identity",
   "(power3)/100", "(power3)/100"
-) 
-
+)
 
 # ------- Write data internally -------
 
-usethis::use_data(expert_subset,
+usethis::use_data(
+  expert_subset,
   analysis_data_param_tables,
   collinearity_subset,
   prediction_ids,

### 2025-10-15 R/standardise_response.R
Lint trailing white space, fix spelling error, fix indentation / formatting style

@@ -59,7 +59,9 @@ standardise_response <- function(data,
   
   # TODO insert checks that appropriate columns exist
   # TODO apply to data and check that all cases accounted for!
-  match.arg(estimate_type, choices = c("Zr", "yi", "y25", "y50", "y75"), several.ok = FALSE)
+  match.arg(estimate_type, 
+            choices = c("Zr", "yi", "y25", "y50", "y75"), 
+            several.ok = FALSE)
   
   cli::cli_h1(c("Computing meta-analysis inputs", 
                 "for {.arg estimate_type} = ", 
@@ -69,7 +71,9 @@ standardise_response <- function(data,
     
     # ------ Convert Effect Sizes to Zr -------
     
-    cli::cli_h2(paste0("Computing standardised effect sizes ", "{.code Zr}", " and variance ", "{.code VZr}"))
+    cli::cli_h2(paste0("Computing standardised effect sizes ", 
+                       "{.code Zr}", 
+                       " and variance ", "{.code VZr}"))
     
     data <- data %>%
       dplyr::mutate(

### 2025-10-16 R/prepare_response_variables.R
RM internal function from being included in family

@@ -196,7 +196,6 @@ prepare_response_variables <- function(data,
 }
 
 #' Wrapper function to standardise response variables
-#' @rdname process_analyst_data
 #' @seealso This internal helper function is called by [prepare_response_variables()]
 #' @importFrom rlang caller_env exec
 #' @keywords internal

### 2025-10-16 R/standardise_response.R
Rm functions from being included in analysis-level family, since operates on dataframe not on vector of calues from dataframe

@@ -37,8 +37,6 @@ NULL
 #' variable will not be standardised, and NA will be returned for that entry in `back_transformed_data`.
 #' @export
 #' @describeIn process_analyst_data Standardise response data for meta-analysis
-#' @family Analysis-level functions
-#' @seealso [est_to_zr()],[assign_transformation_type()], [pred_to_Z()]
 #' @examples
 #' # Standardise effect-sizes for eucalyptus dataset
 #' 
@@ -194,7 +192,6 @@ process_response <- function(data, ...){
 #' @importFrom purrr map
 #' @importFrom rlang is_na
 #' @describeIn process_analyst_data Standardise response data for meta-analysis
-#' @family Analysis-level functions
 log_transform_response <- function(data, sim = 10000L, ...) {
   # TODO insert checks that appropriate columns exist
   # TODO apply to data and check that all cases accounted for!

### 2025-10-16 R/standardise_response.R
Rm separate descriptions for functions on same man page

@@ -1,5 +1,7 @@
 #' Process Response Data for Meta-Analysis
 #' 
+#' @description
+#' This is a family of functions that process response data for meta-analysis, either standardising effect sizes / out-of-sample predictions, or simply formatting the data for meta-analysis without standardisation or transformation.
 #' @param data A tibble of analyst data with a list-column called
 #' @param ... Ignored
 #' @importFrom cli cli_h1 cli_h2 
@@ -142,8 +144,6 @@ standardise_response <- function(data,
 
 #' Process response data for meta-analysis
 #' 
-#' @description
-#' This function generates the response data for meta-analysis without standardising the effect sizes / out-of-sample predictions.
 #' @describeIn process_analyst_data Process response data for meta-analysis but do not standardise effect-sizes
 #' @details
 #' # `process_response()`

### 2025-10-16 R/standardise_response.R
Rm function links that land on same page

@@ -23,7 +23,7 @@ NULL
 #' @details
 #' # `standardise_response()`
 #'
-#' When the `estimate_type` is `"Zr"`, [standardise_response()] standardises 
+#' When the `estimate_type` is `"Zr"`, `standardise_response()` standardises 
 #' effect-sizes with [est_to_zr()], assuming that the `beta_estimate` and 
 #' `beta_SE` values have already been back-transformed to the appropriate scale. #TODO check this.
 #' 
@@ -175,9 +175,9 @@ process_response <- function(data, ...){
 #' 
 #' @param sim a numeric vector of length 1L with the number of simulations that should be passed to [log_transform()]
 #' @details
-#' # [log_transform_response()]
+#' # log_transform_response()
 #' 
-#' maps [log_transform_yi()] onto back-transformed data stored in list-columns within [data]
+#' maps [log_transform_yi()] onto back-transformed data stored in list-columns within `data`
 #' @examples
 #' data(ManyEcoEvo_yi)
 #' ManyEcoEvo_yi %>%

### 2025-10-16 R/assign_transformation_type.R
Add to analysis level functions family

@@ -9,7 +9,7 @@
 #' @export
 #' @import dplyr
 #' @importFrom rlang is_na
-#' @family Back-transformation
+#' @family Back-transformation Analysis-level functions
 #' @seealso [prepare_response_variables_yi(), standardise_response()]. To be called prior to [clean_response_transformation()].
 assign_transformation_type <- function(response_transformation = character(1L),
                                        link_fun = character(1L)) {

### 2025-11-19 manuscript/manuscript/manuscript.Rmd
Update manuscript with edits from @hannahsfraser and @LibbyR

@@
 Many-analyst studies demonstrate how subjective, often arbitrary and usually defensible analysis decisions may influence research results [@silberzahn2018] due to either disagreement among researchers or due to analytic uncertainty about choices such as which observations to include and what data-analysis strategy is most appropriate [@Voracek2019].
-Managing the analysis pipeline of such data is complex and is better implemented with dedicated software.
+Managing the analysis pipelines to implement many-analyst studies is complex and best implemented with dedicated software.
 
-Typical scientific approaches proceed with a single team, and one analytic specification, or at most several specifications implemented.
-Thus the effect of alternative defensible analytic choices that could have been implemented is never known, either because alternative specifications aren't explored, or worse, because analysts / authors implement them but do not publish alternative analysis specifications.
-However, we know from simulations and case studies that researcher degrees of freedom can result in spurious findings [@simmons2011], and these researcher degrees of freedom are susceptible to publication bias, p-hacking and other questionable research practice.
-Similarly, specification curve analysis of published findings have demonstrated that the published conclusion had empirical support from only a small sample of the overall plausible specifications (evidence of spurious findings, and possibly publication bias and p-hacking) [@Simonsohn2019].
-These types of studies are growing in popularity, as we explain below.
+Typical scientific approaches proceed with a single team publishing only one or several ‘analysis specifications,’ or unique sequences of analysis choices.
+Yet, researchers routinely explore and implement multiple plausible analysis specifications, often without disclosing the full set of ‘garden of forking paths’ they explored, and so the effect of alternative defensible analytic choices is unknown.
+The growing body of many-analyst, and ‘multiverse’ or ‘specification analysis’ studies, in which a large decision space containing the full set of combinatorial alternatives is implemented and statistically analysed, reveals that researcher degrees of freedom can result in spurious findings, and are susceptible to publication bias, p-hacking and other questionable research practices when undisclosed [@botvinik-nezer2020; @Simonsohn2020; @Olsson-Collentine].
 
-*ManyEcoEvo* is an R package [@RCoreTeam2022] designed to *facilitate the analysis of* a many-analyst study in ecology and evolutionary biology, the *ManyEcoEvo Project* [@gould2023].
+*ManyEcoEvo* is an R package [@RCoreTeam2022] designed to *facilitate the analysis of* an existing many-analyst study in ecology and evolutionary biology, the *ManyEcoEvo Project* [@Gould2025].
 The purpose of *ManyEcoEvo* is to reproducibly implement the analysis and presentation of results for Gould *et al.* [-@gould2023] such that the 246 analysts as well as other interested researchers may independently reproduce the study's findings.
-The package also aims to facilitate re-analyses and replications of Gould *et al.* [-@gould2023], as well as facilitating the analysis of similar many-analyst style datasets.
+The package also aims to allow re-analyses and replications of Gould *et al.* [-@gould2023], as well as facilitating the analysis of similar many-analyst style datasets.
 
@@
 Analyst survey responses and results are provided in the package GitHub repository (<https://github.com/egouldo/ManyEcoEvo/>), which is also archived on Zenodo (<https://doi.org/10.5281/zenodo.10046153>).
-*ManyEcoEvo* contains tools for data-cleaning and processing tasks encountered when working with with many-analyst style data, functions for implementing and reproducing the analysis described inGould *et al.* [-@gould2023], establishes a structured workflow that facilitates re-analyses and replications of Gould *et al.* [-@gould2023] as well as implementation for new many-analyst studies, including a planned extension of the ManyEcoEvo project.
+*ManyEcoEvo* contains tools for data-cleaning and processing tasks encountered when working with many-analyst style data, functions for implementing and reproducing the analysis described inGould *et al.* [-@gould2023], establishes a structured workflow that facilitates re-analyses and replications of Gould *et al.* [-@gould2023] as well as implementation for new many-analyst studies, including a planned extension of the ManyEcoEvo project.
 
@@
 The last ten years has seen the growing emergence of many-analyst projects, [e.g.
-@silberzahn2018; @botvinik-nezer2020; @huntington-klein2021; @schweinsberg2021; @breznau2022; @hoogeveen2022many; @coretta2023], predominantly in the disciplines of psychology and social and behavioural sciences, however we expect more of these types of studies to be published into the near future across other disciplines.
-Moreover, collaborative and distributed big team open science projects are becoming increasingly common in ecology and evolutionary biology (e.g.
-NutNet/DragNet [nutnet.org/index.php/](https://nutnet.org/index.php/){.uri}, ManyBirds [themanybirds.com](http://themanybirds.com){.uri}) as well as other disciplines [ManyBabies @ManyBabies , ManyPrimates @ManyPrimates] which pose computationally analogous data-manipulation and analysis problems to the many-analyst workflow addressed by the *ManyEcoEvo* approach.
+@silberzahn2018; @botvinik-nezer2020; @huntington-klein2021; @schweinsberg2021; @breznau2022; @hoogeveen2022many; @coretta2023], predominantly in the disciplines of psychology and social and behavioural sciences.
+Given the increasing attention on the reproducibility crisis, it is expected that more of these types of studies will be published in the near future across other disciplines.
+Moreover, collaborative and distributed big team open science projects are increasingly common in ecology and evolutionary biology (e.g.
+NutNet and DragNet [nutnet.org/index.php/](https://nutnet.org/index.php/){.uri}; ManyBirds [themanybirds.com](http://themanybirds.com){.uri}) as well as other disciplines [ManyBabies @ManyBabies , ManyPrimates @ManyPrimates] which pose computationally analogous data-manipulation and analysis problems to the many-analyst workflow addressed by the *ManyEcoEvo* approach.
 
-The *ManyEcoEvo* package was created to implement the analysis for the 'Same Data, Many Analysts in Ecology and Evolutionary Biology' project [@gould2023] and to allow the 246 co-authors and other interested researchers to computationally reproduce our analysis.
-Following [@Marwick2018], [@Vuorre2021] and [@Filazzola2022], we opted to develop this research compendium as an R package as we find it best encapsulates the principles of 'clean code' for effective communication of the science, and therefore facilitates future reproduction, replication and potential synthesis [R packages as research compendia].
-*ManyEcoEvo* was designed for the ManyEcoEvo project, the structured approach it employs establishes a workflow that can be generalised and applied to new many-analyst style data, facilitating replication of Gould *et al.* [-@gould2023], in addition to computational reproduction [@Stoudt2021], as well as new analyses of many-analyst type studies.
+The *ManyEcoEvo* package was created to implement the analysis for the 'Same Data, Many Analysts in Ecology and Evolutionary Biology' project [@Gould2025].
+We opted to develop this research compendium as an R package as we find it best encapsulates the principles of 'clean code' for effective communication of the science [@Filazzola2022], and therefore facilitates future reproduction, replication and potential synthesis [@Marwick2018; @Vuorre2021].
 
@@
 For example, [@Auspurg2021] re-analysed part of the seminal 'Red-Card' many-analyst study examining the influence of whether referees were more likely to give red cards to soccer players with dark skin tone than those with light skin tone [@silberzahn2018].
-By providing the code and data for Gould *et al.* [-@gould2023] the *ManyEcoEvo* package, we aim to facilitate computational reproductions by others in order to verify our results.
-We also aim to facilitate analytic reproductions of this study, wherein *ManyEcoEvo* can be used to re-run the analysis in Gould *et al.* [-@gould2023] with slightly different methods, or subsets of data in order to verify and examine the robustness of our findings.
+By providing the code and data for Gould *et al.* [-@Gould2025] in the *ManyEcoEvo* package, we allow similar re-analyses of the ‘Same Data, Many Analysts in Ecology and Evolutionary Biology’, wherein ManyEcoEvo can be used to re-run the analysis in [@Gould2025] with slightly different methods, or subsets of data in order to verify and examine the robustness of our findings.
+We also provide infrastructure to support others performing many-analyst studies.
 
 We are not aware of any R packages or software in other languages exclusively focussed on facilitating many-analyst style studies.
-Existing many-analyst code if shared, is written as R scripts particular to that study's analysis (e.g.
+Existing many-analyst code if shared, is written as R scripts tailored to that study's analysis (e.g.
 <https://github.com/manybabies/mb1-analysis-public>, <https://github.com/many-speech-analyses/many_analyses>).
-However, there are a range of existing packages with select functionality that addresses various components of many-analyst style analyses, namely meta-analysis, its associated preparation and visualisation, as well as the visualisation component of specification curve analysis / multiverse analysis [@Simonsohn2020; @Steegen2016].
-Following the collection of results from teams conducting independent analyses, the data must be 1.
-cleaned and prepared for 2.
-meta-analysis and other model analysis, which is then 3.
-subjected to model checking, statistic extraction and visualisation [@aczel2021].
+However, there are a range of existing packages with select functionality that addresses various components of many-analyst style analyses, namely meta-analysis, its associated preparation and visualisation, as well as the visualisation component of specification curve analysis / multiverse analysis.
+Our package unites the functions of these packages to provide a selection of tools that are customized to the needs of a many-analyst project.
+In a many-analyst study, multiple researchers submit their analyses and results.
+The submitted data must be cleaned and prepared for meta-analysis and other model analysis, then subjected to model checking, statistic extraction and visualisation [@aczel2021].
 
@@
 
-*ManyEcoEvo* provides custom functions to calculate standardize effect sizes in the form of Fishers' Z correlation scores in preparation for meta-analysis.
+*ManyEcoEvo* provides custom functions to calculate standardised effect sizes in the form of Fishers' Z correlation scores in preparation for meta-analysis.
 While some existing functions exist within other packages [e.g.
-`DescTools::FishersZ()` @DescTools, `DiagTest3Grp::FisherZ.var()` @luo2012diagtest3grp], the method for calculating variance of the standardized effect size in Gould *et al.* [-@gould2023] differed slightly, and we wished to avoid reliance on too many external packages [@wickham2023r, Chapter 10.1].
+`DescTools::FishersZ()` @DescTools, `DiagTest3Grp::FisherZ.var()` @luo2012diagtest3grp], the method for calculating variance of the standardised effect size in Gould *et al.* [-@gould2023] differed slightly, and we wished to avoid reliance on too many external packages [@wickham2023r, Chapter 10.1].
 Should *ManyEcoEvo* users wish to deviate from the effect-size standardisation method used in Gould *et al.* [-@gould2023], they are free to use their own functions provided by other software or custom functions [@harrer2021, see chapter 3 for a range of R code to calculate various effect sizes].
 
-`metafor` [@Viechtbauer:2010ks; @Viechtbauer2017] and `meta` [@Balduzzi2019] R packages are the two most commonly used softwares for undertaking meta-analysis in R [@lortie2020].
-We provide functions for fitting the exact meta-analysis models used in Gould *et al.* [-@gould2023], which were implemented with the *metafor* package [@Viechtbauer2017], however *ManyEcoEvo* users are free to supply alternative model-fitting functions should they wish to deviate from these specified models.
+The two most commonly used software packages for undertaking meta-analysis in R are `metafor::` [@Viechtbauer:2010ks; @Viechtbauer2017] and `meta::` [@Balduzzi2019; @lortie2020].
+We provide functions for fitting the exact meta-analysis models used in Gould *et al.* [-@Gould2025], which were implemented with the `metafor::` package [@Viechtbauer2017].
+However, *ManyEcoEvo* users are free to supply alternative model-fitting functions should they wish to deviate from these specified models.
 After model-fitting and analysis, model checking and extraction of model fit and heterogeneity statistics is implemented using a range of existing packages, including: `performance::` [@ludecke2021], `broom.mixed::` [@Bolker2022], `metafor::` [@Viechtbauer2017].
-*ManyEcoEvo* also draws on existing visualisation packages to implement forest plots [`ggforestplot::`, @ggforestplot; @orchaRd], funnel plots [`metafor::` @Viechtbauer2017], and specification curve analysis plots [`specr::` @Masur2020 ] to examine the influence of analysis specifications on variation in analysis outcomes.
+*ManyEcoEvo* also draws on existing visualisation packages to implement forest plots [`ggforestplot::`, @ggforestplot; @orchaRd], funnel plots [`metafor::` @Viechtbauer2017], and specification curve analysis plots [`specr::` @Masur2020] to examine the influence of analysis specifications on variation in analysis outcomes.
 Select functions from the above packages have been thoughtfully abstracted and coded into wrapper functions according to a principled and structured workflow (described below) for ease of application and generalisation to alternative datasets.
@@
 
-This is the body of the manuscript that will provide a short example of the claims about functionality I've made in the previous sections using the ManyEcoEvo analysis pipeline for correlation coefficients.
+# CRediT Author Statement
 
-# Acknowledgements
+<!-- # Acknowledgements -->
 
-We acknowledge the contributions of all 246 analysts and co-authors of Gould *et al. [-@gould2023]* please see the original manuscript for a full list of contributors to the ManyEcoEvo project.
+<!-- We acknowledge the contributions of all 246 analysts and co-authors of Gould *et al.
+[-@gould2023]* please see the original manuscript for a full list of contributors to the ManyEcoEvo project.
+-->
 
-EG is supported by an Australian Government Research Training Program Scholarship.
+<!-- - [ ] Copy from Many Analysts paper - nothing for HF. -->
 
--   [ ] HF?
--   [ ] SN?
--   [ ] TP?
+<!-- EG is supported by an Australian Government Research Training Program Scholarship. -->
 

### 2025-11-19 manuscript/manuscript/manuscript.Rmd
Update year from 2023 --> 2025, and switch to published many analysts paper citation.

@@
 date: "`r Sys.Date()`"
-year: 2023
+year: 2025
 bibliography: paper.bib
@@
 *ManyEcoEvo* is an R package [@RCoreTeam2022] designed to *facilitate the analysis of* an existing many-analyst study in ecology and evolutionary biology, the *ManyEcoEvo Project* [@Gould2025].
-The purpose of *ManyEcoEvo* is to reproducibly implement the analysis and presentation of results for Gould *et al.* [-@gould2023] such that the 246 analysts as well as other interested researchers may independently reproduce the study's findings.
-The package also aims to allow re-analyses and replications of Gould *et al.* [-@gould2023], as well as facilitating the analysis of similar many-analyst style datasets.
+The purpose of *ManyEcoEvo* is to reproducibly implement the analysis and presentation of results for Gould *et al.* [-Gould2025] such that the 246 analysts as well as other interested researchers may independently reproduce the study's findings.
+The package also aims to allow re-analyses and replications of Gould *et al.* [-Gould2025], as well as facilitating the analysis of similar many-analyst style datasets.
 
-The ManyEcoEvo project is a many-analyst study that aimed to empirically explore the variation in effect sizes and model predictions generated by analytical decisions of different researchers within ecology and evolutionary biology [@gould2023].
+The ManyEcoEvo project is a many-analyst study that aimed to empirically explore the variation in effect sizes and model predictions generated by analytical decisions of different researchers within ecology and evolutionary biology [Gould2025].
 174 analyst teams, comprising 246 analysts, independently investigated the answers to two pre-specified research questions using two previously unpublished datasets, one from conservation ecology, and one from evolutionary biology.
@@
 Analyst survey responses and results are provided in the package GitHub repository (<https://github.com/egouldo/ManyEcoEvo/>), which is also archived on Zenodo (<https://doi.org/10.5281/zenodo.10046153>).
-*ManyEcoEvo* contains tools for data-cleaning and processing tasks encountered when working with many-analyst style data, functions for implementing and reproducing the analysis described inGould *et al.* [-@gould2023], establishes a structured workflow that facilitates re-analyses and replications of Gould *et al.* [-@gould2023] as well as implementation for new many-analyst studies, including a planned extension of the ManyEcoEvo project.
+*ManyEcoEvo* contains tools for data-cleaning and processing tasks encountered when working with many-analyst style data, functions for implementing and reproducing the analysis described inGould *et al.* [-Gould2025], establishes a structured workflow that facilitates re-analyses and replications of Gould *et al.* [-Gould2025] as well as implementation for new many-analyst studies, including a planned extension of the ManyEcoEvo project.
 
@@
 We provide a suite of miscellaneous functions for data cleaning and processing tasks that we expect to be common to the sorts of data collected by many-analyst style studies.
-This was the most time and effort-intensive aspect of the analysis in Gould *et al.* [-@gould2023], and we hope these functions will ease the burden on future researchers conducting many-analyst studies.
+This was the most time and effort-intensive aspect of the analysis in Gould *et al.* [-Gould2025], and we hope these functions will ease the burden on future researchers conducting many-analyst studies.
 
@@
 While some existing functions exist within other packages [e.g.
-`DescTools::FishersZ()` @DescTools, `DiagTest3Grp::FisherZ.var()` @luo2012diagtest3grp], the method for calculating variance of the standardised effect size in Gould *et al.* [-@gould2023] differed slightly, and we wished to avoid reliance on too many external packages [@wickham2023r, Chapter 10.1].
-Should *ManyEcoEvo* users wish to deviate from the effect-size standardisation method used in Gould *et al.* [-@gould2023], they are free to use their own functions provided by other software or custom functions [@harrer2021, see chapter 3 for a range of R code to calculate various effect sizes].
+`DescTools::FishersZ()` @DescTools, `DiagTest3Grp::FisherZ.var()` @luo2012diagtest3grp], the method for calculating variance of the standardised effect size in Gould *et al.* [-Gould2025] differed slightly, and we wished to avoid reliance on too many external packages [@wickham2023r, Chapter 10.1].
+Should *ManyEcoEvo* users wish to deviate from the effect-size standardisation method used in Gould *et al.* [-Gould2025], they are free to use their own functions provided by other software or custom functions [@harrer2021, see chapter 3 for a range of R code to calculate various effect sizes].
 
@@
 <!-- We acknowledge the contributions of all 246 analysts and co-authors of Gould *et al.
-[-@gould2023]* please see the original manuscript for a full list of contributors to the ManyEcoEvo project.
+[-Gould2025]* please see the original manuscript for a full list of contributors to the ManyEcoEvo project.
 -->

### 2025-11-19 R/fit_sorensen_glm.R
Ensure that `cur_group()` isn't called outside of a `mutate()` call

@@ -12,9 +12,21 @@
 #' @importFrom cli cli_h2 cli_alert_info
 #' @importFrom pointblank expect_col_exists
 #' @importFrom purrr simplify
+#' @importFrom rlang try_fetch
 fit_sorensen_glm <- function(data) {
   cli::cli_h2(c("Fitting glm for box-cox transformed outcome with sorensen diversity index as predictor"))
-  cli::cli_alert_info(dplyr::cur_group() %>% purrr::simplify()) # TODO only run when applied within a tibble on a list-col... want fn available on its own
+  # Only run cur_group() when called within a dplyr grouping context
+  rlang::try_fetch(
+    {
+      group_info <- dplyr::cur_group()
+      if (length(group_info) > 0) {
+        cli::cli_alert_info(group_info %>% purrr::simplify())
+      }
+    },
+    error = function(cnd) {
+      # Silently ignore if not in a dplyr grouping context
+    }
+  )
   
   pointblank::expect_col_exists(data, 
                                 columns = c(starts_with("box_cox_abs_"),

### 2025-11-19 R/box_cox_transform.R
Add TODO comments

@@ -16,7 +16,7 @@
 #' @importFrom stringr str_starts
 #' @importFrom tidyr hoist
 #' @seealso [variance_boxcox()], [folded_params()]
-box_cox_transform <- function(data, dataset, outcome_SE_colname) {
+box_cox_transform <- function(data, dataset, outcome_SE_colname) { #TODO undocumented arg 
   # ----- Argument Checking -----
   if ( any(rlang::is_na(data), rlang::is_null(data))) {
     cli::cli_alert_warning(

### 2025-11-19 R/prepare_response_variables.R
Add comments
Process not so clear after a break...

@@ -140,7 +140,7 @@ prepare_response_variables <- function(data,
         tibble(
           dataset = unique(out$dataset),
           fns = list(process_response) %>% 
-            set_names("process_response")
+            set_names("process_response") # Use the `process_response` fn
         )
       
     } else { #yi + standardise and/or log-transform
@@ -152,12 +152,12 @@ prepare_response_variables <- function(data,
           tibble(
             dataset = dataset_log_transform,
             fns = list(log_transform_response) %>% 
-              set_names("log_transform_response")
+              set_names("log_transform_response") # Use the `log_transform_response` fn
           ),
           tibble(
             dataset = dataset_standardise,
             fns = list(standardise_response) %>% 
-              set_names("standardise_response")
+              set_names("standardise_response") # Use the `standardise_response` fn
           )) %>% 
         drop_na() # in case of NULLs
       
@@ -173,7 +173,7 @@ prepare_response_variables <- function(data,
     transform_datasets <- 
       tibble(
         dataset = unique(out$dataset),
-        fns = list(standardise_response)  %>% 
+        fns = list(standardise_response)  %>% # Use the `standardise_response` fn
           set_names("standardise_response")
       )
   } 
@@ -183,7 +183,7 @@ prepare_response_variables <- function(data,
   out <- out %>%
     ungroup() %>%
     left_join(transform_datasets, by = "dataset") %>% 
-    mutate(fns = coalesce(fns, list(process_response))) %>%
+    mutate(fns = coalesce(fns, list(process_response))) %>% # Use the `process_response` fn
     mutate(data = pmap(.l = ., 
                        .f = pmap_wrap,
                        # estimate_type = !!{{estimate_type}},

### 2025-11-19 R/meta_analyse_datasets.R
Qualify arg as optional

@@ -12,7 +12,7 @@
 #' - The deviation scores on transformed categorical ratings but with no intercept (for nice plotting / exploration).
 #'
 #' @param data A nested- dataframe grouped by `dataset` and / or `exclusion_set`, `estimate_type`, containing the list-column of prepared analyst subset data `effects_analysis` ready for meta-analysis.
-#' @param filter_vars A list of expressions to filter the `data` dataframe by. E.g. `rlang::exprs(exclusion_set == "complete", expertise_subset == "All", publishable_subset == "All", collinearity_subset == "All")`
+#' @param filter_vars An optional list of expressions to filter the `data` dataframe by. E.g. `rlang::exprs(exclusion_set == "complete", expertise_subset == "All", publishable_subset == "All", collinearity_subset == "All")`
 #' #' @param outcome_variable A named list containing either/and a list of `dataset`s and their corresponding outcome variables for each value of `dataset`, a list of `estimate_type`s and their corresponding outcome variables for each value of `estimate_type`.
 #' @return A nested dataframe with all columns of object parsed to arg `data`, but with additional columns for the results of each analysis: `MA_mod`, `sorensen_glm`, `box_cox_ratings_cont`, `box_cox_ratings_cat`, `box_cox_rating_cat_no_int`, `uni_mixed_effects`
 #' @export

### 2025-11-19 R/get_forest_plot_data.R
Ensure that forest plot legends are not separate for each aesthetic, and ensure ordering of meta-analytic mean remains in place after fixigng

@@ -17,16 +17,18 @@ get_forest_plot_data <- function(model){
     dplyr::mutate(
       point_shape = 
         ifelse(stringr::str_detect(term, "overall"), 
-               "diamond", 
-               "circle"),
+               "mean", 
+               "study"),
       term = 
         forcats::fct_reorder(term, 
                              estimate) %>% 
         forcats::fct_reorder(., 
                              point_shape,
-                             .desc = TRUE),
+                             .desc = FALSE),
       parameter_type = case_when(str_detect(term, "overall") ~ "mean",
                                  TRUE ~ "study"),
+      # point_shape = factor(point_shape, levels = c("study", "mean")),
+      # parameter_type = factor(parameter_type, levels = c("study", "mean")),
       meta_analytic_mean =  pull(., estimate, type) %>% 
         keep_at(at = "summary")) %>% 
     select(-type, Parameter = term, everything())
@@ -56,7 +58,8 @@ plot_forest <- function(data, intercept = TRUE, MA_mean = TRUE){
     data <- filter(data, Parameter != "overall")
   }
   
-  p <- ggplot(data, aes(y = estimate, 
+  p <- data %>% 
+    ggplot(aes(y = estimate, 
                         x =  Parameter, 
                         ymin = conf.low, 
                         ymax = conf.high,
@@ -69,14 +72,19 @@ plot_forest <- function(data, intercept = TRUE, MA_mean = TRUE){
           text = element_text(family = "Helvetica")#,
           # axis.text.y = element_blank()
     ) +
-    guides(shape = guide_legend(title = NULL), 
-           colour = guide_legend(title = NULL)) +
+    # guides(shape = guide_legend(title = NULL), 
+    #        colour = guide_legend(title = NULL)
+    #        ) +
     coord_flip() +
     ylab(bquote(Standardised~Effect~Size~Z[r])) +
     xlab(element_blank()) +
     # scale_y_continuous(breaks = c(-4,-3,-2,-1,0,1),
     # minor_breaks = seq(from = -4.5, to = 1.5, by = 0.5)) +
-    NatParksPalettes::scale_color_natparks_d("Glacier")
+    # NatParksPalettes::scale_color_natparks_d("Glacier")
+    scale_shape_manual(values = c("study" = 16, "mean" = 23), # circle and diamond
+                       name = NULL) +
+    scale_color_manual(values = c("study" = "#088096", "mean" = "#01353D"),
[…]

### 2025-11-19 manuscript/manuscript/manuscript.Rmd
Complete demo code
-- note! pandoc / rmd error means knit is failing on latex --> PDF.

e.g.: https://github.com/quarto-dev/quarto-cli/issues/10682

@@
 ---
+
+```{r setup, echo=FALSE, message=FALSE}
+# library(ManyEcoEvo)
+devtools::load_all()
+library(dplyr)
+library(metafor)
+library(tidyverse)
+set.seed(1)
+knitr::opts_chunk$set(
+  # collapse = TRUE,
+  # comment = "#>",
+  # fig.width = 7,
+  # fig.height = 5,
+  message = FALSE,
+  warning = FALSE
+)
+```
 
@@
 
-# CRediT Author Statement
+The ManyEcoEvo dataset contains anonymised analyst responses for two research questions: one examining blue tit nestling growth (evolutionary biology) and another examining eucalyptus seedling recruitment (conservation ecology).
+
+```{r}
+# Load the built-in dataset
+data("ManyEcoEvo")
+# Examine the basic structure
+ManyEcoEvo
+glimpse(ManyEcoEvo)
+```
+
+The data is structured with list-columns:
+
+-    `data`: Contains the effect size estimates and analysis metadata for each dataset
+-    `diversity_data`: Contains information about variables used by each analysis team
+
+We will work with a subset of the the Blue tit dataset for illustration purposes.
+
+```{r}
+# Key columns for effect size analysis
+key_cols <- c("id_col", "TeamIdentifier", "beta_estimate", "beta_SE", 
+              "sample_size", "adjusted_df", "dataset", "mixed_model")
+
+analysis_data <- ManyEcoEvo %>% 
+  mutate(
+    data = map(data, ~ .x %>% 
+                  # mutate(study_id = id_col) %>% 
+                 filter(if_all(all_of(key_cols), ~ !is.na(.))) %>% 
+      slice_sample(n = 25) %>%
+      arrange(TeamIdentifier, analysis_id)
+    ),
+    diversity_data = map2(diversity_data, data, ~ 
+      semi_join(.x, .y, by = "id_col")
+    )
+  )
+
+effect_sizes <- analysis_data %>% 
+  pluck("data", 1) %>% 
+  select(all_of(key_cols))
+
+head(effect_sizes)
+```
+
+Each row represents a unique analysis (`id_col`), potentially with multiple analyses per team (`TeamIdentifier`).
+
+## Analysing the Blue tit dataset
+
+### Data Preparation for Meta-analysis
+
+The first step in any meta-analysis is ensuring that the estimands of interest – in this case, effect sizes as correlation coefficients – are on the same response scale to ensure that we are not 'comparing apples to oranges.'
+
+The meta-analyses in the ManyEcoEvo project are performed on Fishers' Z transformed correlation coefficients $Z_r$ with the function `est_to_zr()`, which is called b `standardise_response()`, adding columns of standardised estimates `Zr` and their variance `VZr`:
+
+```{r}
+
+standardised_effect_sizes <- effect_sizes %>% 
+  standardise_response(estimate_type = "Zr")
+
+standardised_effect_sizes %>% glimpse()
+```
+
+Now that we have standardised the analysts' estimates, we can progress to conducting our meta-analysis.
+
+### Meta-analysis and Univariate Analyses
+
+We fit a metaregression to the standardised effect sizes, using the `metafor::` package, with nested random effects:
+
+```{r}
+standardised_effect_sizes <- standardised_effect_sizes %>% 
+    mutate(study_id = id_col)
+
+ma_model <- fit_MA_mv(
+  effects_analysis = standardised_effect_sizes,
+  outcome_colname = "Zr",
+  outcome_SE_colname = "VZr", 
+  estimate_type = "Zr"
+)
+
+summary(ma_model)
+```
+
+#### Calculate inputs for univariate analyses
+
+Calculate deviation of $Z_r$ from the meta-analytic mean for each analysis `id_col`, then Box-Cox transform each deviation score:
+
+```{r}
+effect_size_data <- standardised_effect_sizes %>% 
+  calculate_deviation_score(
+                          meta_analytic_model = ma_model,
+                          outcome_colname = "Zr"
+                          ) %>% 
+  # select(starts_with("abs_deviation_score_"))
+  box_cox_transform(dataset = "blue tit",
+                    outcome_SE_colname = "VZr")
+```
+
+Calculate mean Sorensen's diversity index for each analysis:
+
+```{r}
+
+# Extract diversity data
+diversity_data <- analysis_data %>% 
+  pluck("diversity_data", 1)
+
+mean_sorensen_data <- 
+  diversity_data %>% 
+  calculate_sorensen_diversity_index(.id = "id_col")
+
+mean_sorensen_data
+```
+
+#### Regression on distinctiveness of analysis variables
+
+Join required `mean_diversity_indices` into `effect_size_data` and fit a univariate `glm::` model of deviation scores on mean Sorensen's diversity index.
+Note that the returned model is fitted using `parsnip::`.
+
+```{r}
+effect_size_data <- effect_size_data %>%
+  left_join(mean_sorensen_data, 
+            by = join_by(id_col))
+
+diversity_model <- fit_sorensen_glm(effect_size_data)
+diversity_model # View model summary
+```
+
+#### Visualise Results
+
+Create a forest plot for the blue tit meta-analysis:
+
+```{r include=FALSE}
+get_forest_plot_data(ma_model) %>% 
+  plot_forest(intercept = TRUE)
+```
+
+Create a marginal effects plot for the univariate analysis on the distinctiveness of variables, back-transforming the response variables for easier interpretation:
+
+```{r}
+
+plot_effects_diversity(mod = diversity_model, 
+                       df = effect_size_data , 
+                       back_transform = TRUE)
+```
+
+## Scaling Up
+
+We conducted further univariate regressions to quantify the effects of different analysis features on heterogeneity among analysts' results in addition to the distinctiveness of variables in each analysis, as we illustrated above.
+We also performed the full analysis on a second dataset, the Eucalyptus dataset, and repeated the analysis on different outcome variables (point predictions from analysts' models, not shown in this manuscript), and different subsets of data (e.g., with outliers removed, with poorly rated analyses, among others).
+
+To make conducting multiple analyses easier and to facilitate scaling up the analysis pipeline for repeated application over different analysis questions, data subsets, and outcome variables, we provide a selection of 'wrapper' functions.
+The wrapper frameworks utilise the tidyverse's (ref) list-column data structures and iteration with `purrr::` (ref purrr and R4ds list-cols + iteration).
+Here, we illustrate the simplest case demonstrating this functionality, standardising the estimates in the Blue tit and Eucalyptus datasets, and computing the Sorensen diversity indices, and meta-analysing both datasets (separately) before constructing outputs for further visualisation.
+
+```{r, message =FALSE, warning=FALSE, results = 'hide'}
+
+meta_analysis_results <- 
+  analysis_data %>% 
+  prepare_response_variables(
+    estimate_type = "Zr",
+    dataset_standardise = 
+      c("blue tit", "eucalyptus")) %>% 
+  compute_MA_inputs() %>% 
+  meta_analyse_datasets() %>% 
+  make_viz()
+```
+
+The `make_viz()` function creates many other visualisation and summary objects for easy extraction:
+
+```{r}
+# Extract heterogeneity statistics
+meta_analysis_results %>% 
+  select(dataset, MA_fit_stats) %>%
+    unnest(MA_fit_stats) %>% 
+  drop_na()
+
+# Model fit statistics for univariate model of effect of peer-review ratings on heterogeneity
+meta_analysis_results %>% 
+  filter(model_name == "box_cox_rating_cat") %>% 
+  select(dataset, mod_fit_stats) %>% 
+  unnest(c(dataset, mod_fit_stats))
+```
+
+<!-- # CRediT Author Statement -->
 

### 2025-11-19 manuscript/manuscript/manuscript_examples.qmd

--- 2025-11-19 manuscript/manuscript/manuscript.Rmd
@@
 ---
-# Example from https://joss.readthedocs.io/en/latest/submitting.html
-title: 'ManyEcoEvo: an R package for working with the "Same Data, Different Analysts" Project in Ecology and Evolutionary Biology, and other many-analyst style data'
-tags:
-  - R
-  - meta-analysis
-  - metaresearch
-  - ecology
-  - evolutionary biology
-  - many-analysts
-authors:
-  - name: Elliot Gould
-    orcid: 0000-0003-0872-7098
-    affiliation: "1" 
-  - name: Hannah S. Fraser
-    orcid: 0000-0000-0000-0000
-    affiliation: "1"
-  - name: Shinichi Nakagawa
-    orcid: 0000-0000-0000-0000
-    affiliation: "2"
-  - name: Timothy H. Parker
-    orcid: 0000-0000-0000-0000
-    affiliation: "3"
-affiliations:
- - name: The University of Melbourne
-   index: 1
- - name: The University of New South Wales
-   index: 2
- - name: Whitman College
-   index: 3
-citation_author: Gould and Fraser et al. 
-date: "`r Sys.Date()`"
-year: 2025
-bibliography: paper.bib
-output: 
-  # word_document: default
-  rticles::joss_article:
-    journal: JOSS
-csl: apa.csl
+title: "Introducing the `ManyEcoEvo::` package"
+author: "Elliot Gould"
+format: html
+number-sections: true
+description: |
+  The `ManyEcoEvo` package provides tools for analysing many-analyst style data, specifically designed for the ManyEcoEvo project described in Gould et al.
+(202).
+This vignette demonstrates the core functionality for processing effect size estimates and conducting meta-analyses on data from multiple research teams analysing the same datasets.
+editor: visual
+tidy: styler
 ---
 
-```{r setup, echo=FALSE, message=FALSE}
+```{r setup}
+#| echo: false
+#| message: false
 # library(ManyEcoEvo)
@@
 knitr::opts_chunk$set(
-  # collapse = TRUE,
-  # comment = "#>",
-  # fig.width = 7,
-  # fig.height = 5,
+  collapse = TRUE,
+  comment = "#>",
+  fig.width = 7,
+  fig.height = 5,
   message = FALSE,
@@
 ```
-
-# Summary
-
-Many-analyst studies are a format of crowd-sourced scientific analysis [@schweinsberg2021], where analysts simultaneously, but independently, research the same research question, using the same dataset [@Voracek2019; @silberzahn2018].
-Many-analyst studies demonstrate how subjective, often arbitrary and usually defensible analysis decisions may influence research results [@silberzahn2018] due to either disagreement among researchers or due to analytic uncertainty about choices such as which observations to include and what data-analysis strategy is most appropriate [@Voracek2019].
-Managing the analysis pipelines to implement many-analyst studies is complex and best implemented with dedicated software.
-
-Typical scientific approaches proceed with a single team publishing only one or several ‘analysis specifications,’ or unique sequences of analysis choices.
-Yet, researchers routinely explore and implement multiple plausible analysis specifications, often without disclosing the full set of ‘garden of forking paths’ they explored, and so the effect of alternative defensible analytic choices is unknown.
-The growing body of many-analyst, and ‘multiverse’ or ‘specification analysis’ studies, in which a large decision space containing the full set of combinatorial alternatives is implemented and statistically analysed, reveals that researcher degrees of freedom can result in spurious findings, and are susceptible to publication bias, p-hacking and other questionable research practices when undisclosed [@botvinik-nezer2020; @Simonsohn2020; @Olsson-Collentine].
-
-*ManyEcoEvo* is an R package [@RCoreTeam2022] designed to *facilitate the analysis of* an existing many-analyst study in ecology and evolutionary biology, the *ManyEcoEvo Project* [@Gould2025].
-The purpose of *ManyEcoEvo* is to reproducibly implement the analysis and presentation of results for Gould *et al.* [-Gould2025] such that the 246 analysts as well as other interested researchers may independently reproduce the study's findings.
-The package also aims to allow re-analyses and replications of Gould *et al.* [-Gould2025], as well as facilitating the analysis of similar many-analyst style datasets.
-
-The ManyEcoEvo project is a many-analyst study that aimed to empirically explore the variation in effect sizes and model predictions generated by analytical decisions of different researchers within ecology and evolutionary biology [Gould2025].
-174 analyst teams, comprising 246 analysts, independently investigated the answers to two pre-specified research questions using two previously unpublished datasets, one from conservation ecology, and one from evolutionary biology.
-Analysts investigating the evolutionary biology dataset examined the effect of sibling number and nestling growth of blue tits (*Cyanistes caeruleus*), while analysts investigating the conservation ecology dataset examined the relationship between grass cover and *Eucalyptus* tree seedling recruitment.
-The ManyEcoEvo project quantified the variation in results among analyses using meta-analysis and additionally sought to understand how features of studies such as, variable selection, random effects structures, qualitative and numeric ratings of the methods by peer-reviewers, influenced deviation from the meta-analytic mean.
-
-All raw data sets and metadata provided to independent teams for analysis are publicly archived at <https://osf.io/qjzby> and <https://osf.io/hdv8m>, respectively.
-Analyst survey responses and results are provided in the package GitHub repository (<https://github.com/egouldo/ManyEcoEvo/>), which is also archived on Zenodo (<https://doi.org/10.5281/zenodo.10046153>).
-*ManyEcoEvo* contains tools for data-cleaning and processing tasks encountered when working with many-analyst style data, functions for implementing and reproducing the analysis described inGould *et al.* [-Gould2025], establishes a structured workflow that facilitates re-analyses and replications of Gould *et al.* [-Gould2025] as well as implementation for new many-analyst studies, including a planned extension of the ManyEcoEvo project.
-
-# Statement of Need
-
-The last ten years has seen the growing emergence of many-analyst projects, [e.g.
-@silberzahn2018; @botvinik-nezer2020; @huntington-klein2021; @schweinsberg2021; @breznau2022; @hoogeveen2022many; @coretta2023], predominantly in the disciplines of psychology and social and behavioural sciences.
-Given the increasing attention on the reproducibility crisis, it is expected that more of these types of studies will be published in the near future across other disciplines.
-Moreover, collaborative and distributed big team open science projects are increasingly common in ecology and evolutionary biology (e.g.
-NutNet and DragNet [nutnet.org/index.php/](https://nutnet.org/index.php/){.uri}; ManyBirds [themanybirds.com](http://themanybirds.com){.uri}) as well as other disciplines [ManyBabies @ManyBabies , ManyPrimates @ManyPrimates] which pose computationally analogous data-manipulation and analysis problems to the many-analyst workflow addressed by the *ManyEcoEvo* approach.
-
-The *ManyEcoEvo* package was created to implement the analysis for the 'Same Data, Many Analysts in Ecology and Evolutionary Biology' project [@Gould2025].
-We opted to develop this research compendium as an R package as we find it best encapsulates the principles of 'clean code' for effective communication of the science [@Filazzola2022], and therefore facilitates future reproduction, replication and potential synthesis [@Marwick2018; @Vuorre2021].
-
-The results of some many-analyst studies have been controversial, yielding re-analyses criticising the original implementation of some many-analyst studies.
-For example, [@Auspurg2021] re-analysed part of the seminal 'Red-Card' many-analyst study examining the influence of whether referees were more likely to give red cards to soccer players with dark skin tone than those with light skin tone [@silberzahn2018].
-By providing the code and data for Gould *et al.* [-@Gould2025] in the *ManyEcoEvo* package, we allow similar re-analyses of the ‘Same Data, Many Analysts in Ecology and Evolutionary Biology’, wherein ManyEcoEvo can be used to re-run the analysis in [@Gould2025] with slightly different methods, or subsets of data in order to verify and examine the robustness of our findings.
-We also provide infrastructure to support others performing many-analyst studies.
-
-We are not aware of any R packages or software in other languages exclusively focussed on facilitating many-analyst style studies.
-Existing many-analyst code if shared, is written as R scripts tailored to that study's analysis (e.g.
-<https://github.com/manybabies/mb1-analysis-public>, <https://github.com/many-speech-analyses/many_analyses>).
-However, there are a range of existing packages with select functionality that addresses various components of many-analyst style analyses, namely meta-analysis, its associated preparation and visualisation, as well as the visualisation component of specification curve analysis / multiverse analysis.
-Our package unites the functions of these packages to provide a selection of tools that are customized to the needs of a many-analyst project.
-In a many-analyst study, multiple researchers submit their analyses and results.
-The submitted data must be cleaned and prepared for meta-analysis and other model analysis, then subjected to model checking, statistic extraction and visualisation [@aczel2021].
-
-We provide a suite of miscellaneous functions for data cleaning and processing tasks that we expect to be common to the sorts of data collected by many-analyst style studies.
-This was the most time and effort-intensive aspect of the analysis in Gould *et al.* [-Gould2025], and we hope these functions will ease the burden on future researchers conducting many-analyst studies.
-
-*ManyEcoEvo* provides custom functions to calculate standardised effect sizes in the form of Fishers' Z correlation scores in preparation for meta-analysis.
-While some existing functions exist within other packages [e.g.
-`DescTools::FishersZ()` @DescTools, `DiagTest3Grp::FisherZ.var()` @luo2012diagtest3grp], the method for calculating variance of the standardised effect size in Gould *et al.* [-Gould2025] differed slightly, and we wished to avoid reliance on too many external packages [@wickham2023r, Chapter 10.1].
-Should *ManyEcoEvo* users wish to deviate from the effect-size standardisation method used in Gould *et al.* [-Gould2025], they are free to use their own functions provided by other software or custom functions [@harrer2021, see chapter 3 for a range of R code to calculate various effect sizes].
-
-The two most commonly used software packages for undertaking meta-analysis in R are `metafor::` [@Viechtbauer:2010ks; @Viechtbauer2017] and `meta::` [@Balduzzi2019; @lortie2020].
-We provide functions for fitting the exact meta-analysis models used in Gould *et al.* [-@Gould2025], which were implemented with the `metafor::` package [@Viechtbauer2017].
-However, *ManyEcoEvo* users are free to supply alternative model-fitting functions should they wish to deviate from these specified models.
-After model-fitting and analysis, model checking and extraction of model fit and heterogeneity statistics is implemented using a range of existing packages, including: `performance::` [@ludecke2021], `broom.mixed::` [@Bolker2022], `metafor::` [@Viechtbauer2017].
-*ManyEcoEvo* also draws on existing visualisation packages to implement forest plots [`ggforestplot::`, @ggforestplot; @orchaRd], funnel plots [`metafor::` @Viechtbauer2017], and specification curve analysis plots [`specr::` @Masur2020] to examine the influence of analysis specifications on variation in analysis outcomes.
-Select functions from the above packages have been thoughtfully abstracted and coded into wrapper functions according to a principled and structured workflow (described below) for ease of application and generalisation to alternative datasets.
-
-# Same Data, Different Analysts: variation in effect sizes due to analytical decisions in ecology and evolutionary biology
 
@@
 
-## Analysing the Blue tit dataset
+# Analysing the Blue tit dataset
 
-### Data Preparation for Meta-analysis
+## Data Preparation for Meta-analysis
 
@@
 
-### Meta-analysis and Univariate Analyses
+## Meta-analysis and Univariate Analyses
 
@@
 
-#### Calculate inputs for univariate analyses
+### Calculate inputs for univariate analyses
 
@@
 
-#### Regression on distinctiveness of analysis variables
+### Regression on distinctiveness of analysis variables
 
@@
 
-#### Visualise Results
+### Visualise Results
 
@@
 
-```{r include=FALSE}
+```{r}
 get_forest_plot_data(ma_model) %>% 
@@
 
-## Scaling Up
+# Scaling Up
 
@@
 
-```{r, message =FALSE, warning=FALSE, results = 'hide'}
-
+```{r}
+#| message: false
+#| warning: false
+#| results: hide
 meta_analysis_results <- 
@@
 ```
-
-<!-- # CRediT Author Statement -->
-
-<!-- # Acknowledgements -->
-
-<!-- We acknowledge the contributions of all 246 analysts and co-authors of Gould *et al.
-[-Gould2025]* please see the original manuscript for a full list of contributors to the ManyEcoEvo project.
--->
-
-<!-- - [ ] Copy from Many Analysts paper - nothing for HF. -->
-
-<!-- EG is supported by an Australian Government Research Training Program Scholarship. -->
-
-# References
